---
title: 'Memory Specificity Analyses: Experiment 1 (Partial CF Learning Model)'
author: "Kate Nussenbaum"
date: "6/13/24"
output: 
  html_document:
    df_print: paged
    theme: flatly
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{=html}
<style type="text/css">
h1.title {
font-size: 38px;
}
h1 { /* Header 1 */
font-size: 28px;
}
h2 { /* Header 2 */
font-size: 22px;
}
h3 { /* Header 3 */
font-size: 18px;
}

</style>
```

------------------------------------------------------------------------

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, cache = T)
knitr::opts_chunk$set(fig.path = "figures/partial_cf_model/")
knitr::opts_chunk$set(fig.height = 4, dpi = 600)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r load needed libraries}
library(tidyverse)
library(glue)
library(afex)
library(ggpubr)
library(pander)
library(sjPlot)
library(see)
library(latex2exp)
library(pROC)
```

```{r define functions}

#z-score variables
scale_this <- function(x){
  (x - mean(x, na.rm=TRUE)) / sd(x, na.rm=TRUE)
}

#standard error
se <- function(x){
    sd(x, na.rm = T)/sqrt(length(x))
}

#display model stats
tab_model_glmer <- function(model_name){
    tab_model(model_name,
          digits = 4,
          show.intercept = F,
          show.est = T,
          show.ci = .95,
          show.se = F,
          show.stat = F,
          show.p = F,
          string.se = "SE")
}

```

```{r plot theme}

#define colors to use for plots
color4 =  "#d94f70"
color5 = "#f88f58"
color3 = "#45b5aa"
color1 = "#FFCA4B"
color2 = "#6364a5"

#define plotting theme
mem_theme <- theme(panel.background = element_rect(fill='transparent'),
                   axis.line = element_line(color='black'),
                   panel.border = element_rect(color = 'black', fill = "transparent"),
                   panel.grid.minor = element_line(color='transparent'),
                   axis.title.x = element_text(size=16, vjust=-.25),
                   axis.title.y = element_text(size=16, vjust=1),
                   axis.text.x = element_text(size=12, colour="black"),
                   axis.text.y = element_text(size=12, colour="black"),
                   legend.text=element_text(size=12),
                   legend.title = element_text(size = 14),
                   plot.title = element_text(size=16, face = "bold", hjust = .5), 
                   strip.text.x = element_text(size=12), 
                   strip.text.y = element_text(size=12), 
                   strip.background = element_rect(colour= "black", fill = "transparent"))
```

# Import and process data

```{r import age data}

#read in subject ages
sub_ages <- read_csv(glue('data/e1_sub_ages.csv')) 

#create list of all included subjects with subject ids, age, age group
subject_list <- sub_ages %>%
    mutate(age = as.numeric(age)) %>%
    mutate(age_group = case_when(age < 13 ~ "Children",
                                 age >= 13 & age < 18 ~ "Adolescents",
                                 age >= 18 ~ "Adults")) %>%
    mutate(age_group = factor(age_group, levels = c("Children", "Adolescents", "Adults")))
```

```{r import and format learning data}
learning_data <- read_csv('data/e1_learning_data.csv') %>%
    mutate(reward_condition = as.factor(case_when(block_condition == 1 ~ "Category-Predictive",
                                        block_condition == 2 ~ "Exemplar-Predictive"))) %>%
    group_by(subject_id, task_block, stimulus) %>% 
    mutate(stimulus_repetition = rank(trial_index),
           approach_reward = parse_number(approach_reward)) %>% 
    ungroup() %>%
    mutate(correct_response = case_when(approach_reward > 0 ~ "1",
                                        approach_reward < 0 ~ "0"),
           correct_response_made = case_when(key_press == correct_response ~ 1,
                                             key_press != correct_response ~ 0))

#add within-block trial and within-condition block order
learning_data <- learning_data %>%
    group_by(subject_id, task_block) %>%
    mutate(learning_trial = rank(trial_index)) %>%
    ungroup() %>%
    group_by(subject_id, block_condition) %>%
    mutate(within_condition_block_num = as.numeric(factor(rank(block_order))))

# add age
learning_data <- full_join(learning_data, subject_list, by = c('subject_id'))

#factor subject id
learning_data$subject_id <- factor(learning_data$subject_id)
```



# Memory
```{r import and format memory data}

#combine and process
memory_data <-  read_csv('data/e1_memory_data.csv') %>%
    filter(task_block != "practice") %>%
    filter(is.na(mem_acc) == F)

#relabel foil type and reward condition
memory_data$foil_type <- factor(memory_data$foil_type, levels = c("old", "exemplar", "category"),
                                  labels = c("Old", "Novel Exemplar", "Novel Category"))

memory_data$reward_condition <- factor(memory_data$block_condition,
                                            levels = c(1, 2),
                                            labels = c("Category-Predictive", "Exemplar-Predictive"))

#combine with subject ages
memory_data <- inner_join(memory_data, subject_list, by = c("subject_id"))
```

```{r fit ROC curves for each participant and derive AUC}
exemplar_AUCs <- memory_data %>%
    filter(foil_type != "Novel Category") %>%
    select(subject_id, memory_delay, age_group, reward_condition, correct_mem_response, conf_rating) %>%
    group_by(subject_id, memory_delay, age_group, reward_condition) %>%
    mutate(exemplar = as.numeric(roc(correct_mem_response ~ conf_rating)$auc)) %>%
    select(subject_id, memory_delay, reward_condition, exemplar) %>%
    unique()

category_AUCs <- memory_data %>%
    filter(foil_type != "Novel Exemplar") %>%
    select(subject_id, memory_delay, age_group, reward_condition, correct_mem_response, conf_rating) %>%
    group_by(subject_id, memory_delay, age_group, reward_condition) %>%
    mutate(category = as.numeric(roc(correct_mem_response ~ conf_rating)$auc)) %>%
    select(subject_id, memory_delay, reward_condition, category) %>%
    unique()


#combine AUCs into single data frame
participant_AUCs <- full_join(exemplar_AUCs, category_AUCs, by = c("subject_id", "memory_delay", "age_group", "reward_condition")) %>%
    pivot_longer(cols = c(exemplar, category),
                 names_to = "foil_type",
                 values_to = "AUC")

aucs <- full_join(participant_AUCs, subject_list, by = c("subject_id", "age_group")) 
```

# RL modeling

# Choice weights from model with partial counterfactual learning

```{r cbm parameter ests fourB_oneQ_CF}

#read in param ests
param_ests <- read_csv("data/model_estimates/params_fourB_oneQ_CF.csv")

#merge with age
param_ests <- full_join(param_ests, subject_list, by = c("subject_id"))
```

### Figure: Distribution of choice weights from CF model

```{r beta histogram cf, fig.width = 7, fig.height = 5}

#pivot longer
beta_ests <- param_ests %>%
    pivot_longer(cols = c(beta_c_cCond: beta_e_eCond),
                 names_to = "beta_parameter",
                 names_prefix = "beta_",
                 values_to = "est") %>%
    separate(beta_parameter, into = c("beta_val", "block_condition"), sep = "_") %>%
    drop_na()

beta_ests$abstraction <- factor(beta_ests$beta_val,
                                levels = c("c", "e"),
                                labels = c("category", "exemplar"))

beta_ests$reward_condition <- factor(beta_ests$block_condition,
                                levels = c("cCond", "eCond"),
                                labels = c("Category-Predictive", "Exemplar-Predictive"))

#find means to add to plot
beta_means <- beta_ests %>%
    group_by(reward_condition, abstraction, age_group) %>%
    summarize(mean_est = mean(est, na.rm = T))

#plot
beta_histogram <- ggplot(beta_ests, aes(x = est)) +
    facet_grid(rows = vars(abstraction), cols = vars(age_group)) + 
    geom_histogram(position = "identity", color = 'black', aes(fill = reward_condition), alpha = .4) +
    geom_vline(data = beta_means, aes(xintercept = mean_est, color = reward_condition), linewidth = 2) + 
    xlab("Choice Weight Magnitude") +
    ylab("Number of Participants") +
    scale_y_continuous(breaks = c(0, 3, 6, 9)) +
    scale_fill_manual(values = c(color1, color2), name = "Block Condition") +
    scale_color_manual(values = c(color1, color2), name = "Block Condition") +
    mem_theme +
    theme(legend.position = "top")
beta_histogram
```

```{r simple choice weights cf fig no age, fig.width = 7, fig.height = 5}

#find means to add to plot
beta_means <- beta_ests %>%
    group_by(reward_condition, abstraction, age_group) %>%
    summarize(mean_est = mean(est, na.rm = T))

#plot
choice_weights_plot_no_age <- ggplot(beta_ests, aes(y = est, x = abstraction, fill = reward_condition)) +
   # facet_grid(cols = vars(age_group)) + 
    geom_boxplot() +
    xlab("Choice Weight") +
    ylab("Estimate") +
   # scale_y_continuous(breaks = c(0, 3, 6, 9)) +
    scale_fill_manual(values = c(color1, color2), name = "Block Condition") +
  #  scale_color_manual(values = c(color1, color2), name = "Block Condition") +
    mem_theme +
    theme(legend.position = "right")
choice_weights_plot_no_age
```

### Model: Choice weights by block condition and age

```{r fit choice weight by age model cf}

#scale age
beta_ests$age_scaled <- scale_this(beta_ests$age)

#do betas change across conditions and by age?
beta.age.model <- mixed(est ~ abstraction * reward_condition * age_scaled + (1|subject_id),
                            method = "S",
                           data = beta_ests)
nice(beta.age.model) 
```

```{r display choice weight by age model cf}
beta.age.model.lmer <- mixed(est ~ abstraction * reward_condition * age_scaled + (1|subject_id),
                            method = "S",
                           data = beta_ests,
                           return = "merMod")

tab_model_glmer(beta.age.model.lmer)
```

### Model: Exemplar choice weights across conditions

```{r fit exemplar choice weight across conditions model cf}

#filter and scale age
exemp_beta_ests <- beta_ests %>%
    filter(abstraction == "exemplar")

#do exemplar choice weights change across conditions?
beta.model.exemp <- mixed(est ~ reward_condition + (1|subject_id),
                            method = "S",
                           data = exemp_beta_ests)
nice(beta.model.exemp) 
```

```{r display exemplar choice weight by age model cf}
beta.age.model.exemp.lmer <- mixed(est ~ reward_condition + (1|subject_id),
                                   method = "S",
                                   data = exemp_beta_ests,
                                   return = "merMod")

tab_model_glmer(beta.age.model.exemp.lmer)
```

### Model: Category choice weights across conditions

```{r fit category choice weight  model cf}
#filter and scale age
cat_beta_ests <- beta_ests %>%
    filter(abstraction == "category")

#do betas change across conditions and by age?
beta.age.model.cat <- mixed(est ~ reward_condition + (1|subject_id),
                            method = "S",
                           data = cat_beta_ests)
nice(beta.age.model.cat) 

# reward condition
# reward condition x age interaction
```

```{r display category choice weight model cf}
beta.age.model.cat.lmer <- mixed(est ~ reward_condition  + (1|subject_id),
                                   method = "S",
                                   data = cat_beta_ests,
                                   return = "merMod")

tab_model_glmer(beta.age.model.cat.lmer)
```

### Relations between choice weights and points earned

```{r choice weights points data processing cf}
participant_points <- learning_data %>%
    group_by(subject_id, reward_condition) %>%
    summarize(total_points = sum(points, na.rm = T)) 

#convert subject_id to factor
beta_ests$subject_id <- factor(beta_ests$subject_id)

#join
beta_ests_points <- full_join(participant_points, beta_ests, by = c("subject_id", "reward_condition"))
```

```{r fit choice weights points model cf}

#drop na
beta_ests_points <- beta_ests_points %>%
    select(est, total_points, age, age_group, abstraction, reward_condition, subject_id) %>%
    drop_na()

#scale
beta_ests_points$beta_scaled <- scale_this(beta_ests_points$est)
beta_ests_points$age_scaled <- scale_this(beta_ests_points$age)

#do beta values predict points?
beta_points_model <- mixed(total_points ~ age_scaled * beta_scaled * abstraction * reward_condition + (1|subject_id),
                           data = beta_ests_points)
nice(beta_points_model)

# effects of 
# age
# beta
# age x beta
# abstraction x block condition x beta
```

```{r fit separate regressions to look at how exemplar and category choice weights influence points across conditions cf}

#drop na
beta_ests_points_c_c <- beta_ests_points %>%
    filter(reward_condition == "Category-Predictive",
           abstraction == "category")

beta_ests_points_e_c <- beta_ests_points %>%
    filter(reward_condition == "Category-Predictive",
           abstraction == "exemplar")

beta_ests_points_c_e <- beta_ests_points %>%
    filter(reward_condition == "Exemplar-Predictive",
           abstraction == "category")

beta_ests_points_e_e <- beta_ests_points %>%
    filter(reward_condition == "Exemplar-Predictive",
           abstraction == "exemplar")

#do beta values predict points?
beta_points_model1 <- lm(total_points ~ est, data = beta_ests_points_c_c)
beta_points_model2 <- lm(total_points ~ est, data = beta_ests_points_e_c)
beta_points_model3 <- lm(total_points ~ est, data = beta_ests_points_c_e)
beta_points_model4 <- lm(total_points ~ est, data = beta_ests_points_e_e)

summary(beta_points_model1) #sig
summary(beta_points_model2) #sig
summary(beta_points_model3) #not sig
summary(beta_points_model4) #sig
```

### Figure 2D: Effect of choice weights on points earned

```{r points and choice weights plot cf, fig.height = 5}
points_beta_plot <- ggplot(beta_ests_points, aes(x = est, y = total_points, color = abstraction)) +
    facet_grid(cols = vars(reward_condition)) +
    geom_point() +
    geom_smooth(method = "lm", aes(fill = abstraction)) +
    scale_color_manual(values = c(color1, color2), name = "Choice Weight") + 
    scale_fill_manual(values = c(color1, color2), name = "Choice Weight") +
    ylab("Total Points Earned") +
    xlab("Choice Weight Magnitude") +
    mem_theme +
    theme(legend.position = "top")
points_beta_plot
```

# Relations between learning and memory

## Do choice weights relate to memory?

```{r auc beta data processing cf}

#select relevant beta variables
beta_ests_mem <- beta_ests %>%
    select(subject_id, reward_condition, abstraction, est)

#select relevant memory variables
temp <- aucs %>%
    select(subject_id, memory_delay, reward_condition, abstraction = foil_type, age_group, age, AUC)

```

### Model: AUC by age, exemplar choice weights, specificity, block condition

```{r fit auc exemplar choice weights model cf}

#get exemplar weights
exemplar_weights <- beta_ests_mem %>%
    filter(abstraction == "exemplar") %>%
    select(subject_id, reward_condition, est)

temp$subject_id <- factor(temp$subject_id)

#join data
auc_beta_exemplar <- full_join(temp, exemplar_weights, by = c("subject_id", "reward_condition"))

#scale relevant variables
auc_beta_exemplar$age_scaled <-scale_this(auc_beta_exemplar$age)
auc_beta_exemplar$beta_scaled <-scale_this(auc_beta_exemplar$est)

#fit model
auc_beta_exemplar_model <- mixed(AUC ~ age_scaled * beta_scaled * abstraction * reward_condition + (1|subject_id),
                                  method = "S",
                                  data = auc_beta_exemplar)
nice(auc_beta_exemplar_model)

#effects of:
# beta
# abstraction
# reward condition
# age x beta
# beta x reward condition
# age x beta x reward condition (marginal)

```

```{r display auc exemplar choice weights model cf}

auc_beta_exemplar_model.lmer <- mixed(AUC ~ age_scaled * beta_scaled * abstraction * reward_condition + (1|subject_id),
                                  method = "S",
                                  data = auc_beta_exemplar,
                                  return = "merMod")

tab_model_glmer(auc_beta_exemplar_model.lmer)
```

## Figure 3C: AUC by exemplar choice weights - model effects

```{r plot auc by exemplar choice weights model effects cf, fig.width = 10}

sjPlot::set_theme( 
    base = theme_classic(),
    legend.item.backcol = "transparent",
    geom.boxoutline.color = "black",
    axis.textsize = 1,
    axis.textcolor = "black",
    axis.title.color = "black",
    axis.title.size = 1.1,
    axis.title.x.vjust = -.25,
    axis.title.y.vjust = 1,
    legend.title.size = 1.05)

plot_model(auc_beta_exemplar_model.lmer, type = "pred",
           terms = c("beta_scaled", "age_scaled", "reward_condition", "abstraction"),
           colors = c("#FFCA4B", "#6364a5", "#45b5aa")) +
    scale_color_manual(values = c(color1, color2, color3), name = "Age",
                       labels = c("~ 11 years old",
                                  "~ 16 years old",
                                  "~ 21 years old"
                                  )) +
        scale_fill_manual(values = c(color1, color2, color3), name = "Age",
                       labels = c("~ 11 years old",
                                  "~ 16 years old",
                                  "~ 21 years old"
                                  )) 
```

## Model: AUC by age, category choice weights, specificity, block condition

```{r fit auc category choice weights model cf}

#get relevant variables
cat_weights <- beta_ests_mem %>%
    filter(abstraction == "category") %>%
    select(subject_id, reward_condition, est)

#join data
auc_beta_cat <- full_join(temp, cat_weights, by = c("subject_id", "reward_condition")) 

#scale
auc_beta_cat$age_scaled <-scale_this(auc_beta_cat$age)
auc_beta_cat$beta_scaled <-scale_this(auc_beta_cat$est)

#fit model
auc_beta_cat_model <- mixed(AUC ~ age_scaled * beta_scaled * abstraction * reward_condition + (1|subject_id),
                                  method = "S",
                                  data = auc_beta_cat)
nice(auc_beta_cat_model)

# effects of:
# age 
# abstraction
# reward condition
# beta x abstraction (marginal)

```

```{r display auc category choice weights model cf}

auc_beta_cat_model.lmer <- mixed(AUC ~ age_scaled * beta_scaled * abstraction * reward_condition + (1|subject_id),
                                  method = "S",
                                  data = auc_beta_cat,
                                  return = "merMod")

tab_model_glmer(auc_beta_cat_model.lmer)
```

## Figure 3C: AUC by category choice weights: model effects

```{r plot auc by cat choice weights model effects cf, fig.width = 10}

sjPlot::set_theme( 
    base = theme_classic(),
    legend.item.backcol = "transparent",
    geom.boxoutline.color = "black",
    axis.textsize = 1,
    axis.textcolor = "black",
    axis.title.color = "black",
    axis.title.size = 1.1,
    axis.title.x.vjust = -.25,
    axis.title.y.vjust = 1,
    legend.title.size = 1.05)

plot_model(auc_beta_cat_model.lmer, type = "pred",
           terms = c("beta_scaled", "age_scaled", "reward_condition", "abstraction"),
           colors = c("#FFCA4B", "#6364a5", "#45b5aa")) +
    scale_color_manual(values = c(color1, color2, color3), name = "Age",
                       labels = c("~ 11 years old",
                                  "~ 16 years old",
                                  "~ 21 years old"
                                  )) +
        scale_fill_manual(values = c(color1, color2, color3), name = "Age",
                       labels = c("~ 11 years old",
                                  "~ 16 years old",
                                  "~ 21 years old"
                                  )) 
```

## Figure (for presentation): Category and exemplar memory by exemplar choice weights

```{r exemplar choice weights and memory cf}

exemplar_choice_weight_mem_plot <- ggplot(auc_beta_exemplar, aes(x = beta_scaled, y = AUC, color = abstraction)) +
    geom_point() +
    geom_smooth(method = lm, aes(fill = abstraction)) +
    xlab("Exemplar Choice Weight") +
    ylab("Memory Performance") +
    scale_color_manual(values = c(color1, color2), name = "Memory Specificity") +
    scale_fill_manual(values = c(color1, color2), name = "Memory Specificity") +
    mem_theme
exemplar_choice_weight_mem_plot

```

```{r exemplar choice weights and memory by age group cf, fig.width = 10}

exemplar_choice_weight_mem_age_plot <- ggplot(auc_beta_exemplar, aes(x = beta_scaled, y = AUC, color = abstraction)) +
    facet_wrap(~age_group, scales = "free") +
    geom_point() +
    geom_smooth(method = lm, aes(fill = abstraction)) +
    xlab("Exemplar Choice Weight") +
    ylab("Memory Performance") +
    scale_color_manual(values = c(color1, color2), name = "Memory Specificity") +
    scale_fill_manual(values = c(color1, color2), name = "Memory Specificity") +
    mem_theme
exemplar_choice_weight_mem_age_plot
```
