---
title: 'Memory Specificity Analyses: Experiment 1'
author: "Kate Nussenbaum"
date: "3/27/25"
output: 
  html_document:
    df_print: paged
    theme: flatly
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{=html}
<style type="text/css">
h1.title {
font-size: 38px;
}
h1 { /* Header 1 */
font-size: 28px;
}
h2 { /* Header 2 */
font-size: 22px;
}
h3 { /* Header 3 */
font-size: 18px;
}

</style>
```

------------------------------------------------------------------------

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, cache = T)
knitr::opts_chunk$set(fig.path = "figures/")
knitr::opts_chunk$set(fig.height = 4, dpi = 600)
knitr::opts_chunk$set(dev = 'svg')
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r load needed libraries}
library(tidyverse)
library(glue)
library(afex)
library(ggpubr)
library(pander)
library(sjPlot)
library(see)
library(latex2exp)
library(pROC)
```

```{r define functions}

#z-score variables
scale_this <- function(x){
  (x - mean(x, na.rm=TRUE)) / sd(x, na.rm=TRUE)
}

#standard error
se <- function(x){
    sd(x, na.rm = T)/sqrt(length(x))
}

#display model stats
tab_model_glmer <- function(model_name){
    tab_model(model_name,
          digits = 4,
          show.intercept = F,
          show.est = T,
          show.ci = .95,
          show.se = F,
          show.stat = F,
          show.p = F,
          string.se = "SE")
}

```

```{r plot theme}

#define colors to use for plots
color4 =  "#d94f70"
color5 = "#f88f58"
color3 = "#45b5aa"
color1 = "#FFCA4B"
color2 = "#6364a5"

#define plotting theme
mem_theme <- theme(panel.background = element_rect(fill='transparent'),
                   axis.line = element_line(color='black'),
                   panel.border = element_rect(color = 'black', fill = "transparent"),
                   panel.grid.minor = element_line(color='transparent'),
                   axis.title.x = element_text(size=16, vjust=-.25),
                   axis.title.y = element_text(size=16, vjust=1),
                   axis.text.x = element_text(size=12, colour="black"),
                   axis.text.y = element_text(size=12, colour="black"),
                   legend.text=element_text(size=12),
                   legend.title = element_text(size = 14),
                   plot.title = element_text(size=16, face = "bold", hjust = .5), 
                   strip.text.x = element_text(size=12), 
                   strip.text.y = element_text(size=12), 
                   strip.background = element_rect(colour= "black", fill = "transparent"))
```

# Import and process data

```{r import age data}

#read in subject ages
sub_ages <- read_csv(glue('data/e1_sub_ages.csv')) 

#create list of all included subjects with subject ids, age, age group
subject_list <- sub_ages %>%
    mutate(age = as.numeric(age)) %>%
    mutate(age_group = case_when(age < 13 ~ "Children",
                                 age >= 13 & age < 18 ~ "Adolescents",
                                 age >= 18 ~ "Adults")) %>%
    mutate(age_group = factor(age_group, levels = c("Children", "Adolescents", "Adults")))
```

```{r import and format learning data}
learning_data <- read_csv('data/e1_learning_data.csv') %>%
    mutate(reward_condition = as.factor(case_when(block_condition == 1 ~ "Category-Predictive",
                                        block_condition == 2 ~ "Exemplar-Predictive"))) %>%
    group_by(subject_id, task_block, stimulus) %>% 
    mutate(stimulus_repetition = rank(trial_index),
           approach_reward = parse_number(approach_reward)) %>% 
    ungroup() %>%
    mutate(correct_response = case_when(approach_reward > 0 ~ "1",
                                        approach_reward < 0 ~ "0"),
           correct_response_made = case_when(key_press == correct_response ~ 1,
                                             key_press != correct_response ~ 0))

#add within-block trial and within-condition block order
learning_data <- learning_data %>%
    group_by(subject_id, task_block) %>%
    mutate(learning_trial = rank(trial_index)) %>%
    ungroup() %>%
    group_by(subject_id, block_condition) %>%
    mutate(within_condition_block_num = as.numeric(factor(rank(block_order))))

# add age
learning_data <- full_join(learning_data, subject_list, by = c('subject_id'))

#factor subject id
learning_data$subject_id <- factor(learning_data$subject_id)
```

# Learning

## Model: Correct responses by age, trial, block number, and block condition

```{r fit correct response regression}

#filter data
learning_cr_model_data <- learning_data %>%
    filter(block_condition == "2" | cat_type != "neutral") %>% #exclude 'neutral' category from cat-predictive
    filter(rt > 0) %>% #only include trials where responses were made
    select(correct_response_made, age, learning_trial, reward_condition, block_order, within_condition_block_num, subject_id) %>%
    drop_na()

#scale variables
learning_cr_model_data$age_scaled <- scale_this(learning_cr_model_data$age)
learning_cr_model_data$learning_trial_scaled <- scale_this(learning_cr_model_data$learning_trial)
learning_cr_model_data$block_number_scaled <- scale_this(learning_cr_model_data$within_condition_block_num)

#run model
learning_cr_model <- mixed(correct_response_made ~ age_scaled * learning_trial_scaled * reward_condition * block_number_scaled + (learning_trial_scaled * reward_condition * block_number_scaled || subject_id),
                           data = learning_cr_model_data,
                           family = "binomial",
                           method = "LRT",
                           expand_re = T,
                           control = glmerControl(optimizer = "bobyqa"))
nice(learning_cr_model)

# significant effects of:
# age
# trial
# block condition
# block number
# age x trial
# age x block condition
# trial x block condition
# trial x block number
# block condition x block number
# age x trial x block condition
```

```{r display learning model}
learning_cr_model.glmer <- mixed(correct_response_made ~ age_scaled * learning_trial_scaled * reward_condition * block_number_scaled + (learning_trial_scaled * reward_condition * block_number_scaled || subject_id),
                           data = learning_cr_model_data,
                           family = "binomial",
                           method = "LRT",
                           expand_re = T,
                           control = glmerControl(optimizer = "bobyqa"),
                           return = "merMod")

tab_model_glmer(learning_cr_model.glmer)
```

## Figure 2A: Correct response by block condition, stimulus repetition, and age group

```{r plot learning by age group}

# Plot correct response as a function of reward condition and stimulus repetition 
correct_response_summary_sub <- learning_data %>%
    filter(block_condition == "2" | cat_type != "neutral") %>%
    filter(rt > 0) %>%
    group_by(reward_condition, stimulus_repetition, subject_id, age_group) %>%
    summarize(mean_correct = mean(correct_response_made, na.rm = T))

correct_response_summary <- correct_response_summary_sub  %>%
    group_by(reward_condition, stimulus_repetition, age_group) %>%
    summarize(group_mean_correct = mean(mean_correct, na.rm = T),
              se_correct = se(mean_correct))

#group means
correct_response_plot <- ggplot(correct_response_summary_sub, 
                                    aes(x = as.factor(stimulus_repetition), 
                                        fill = reward_condition,
                                        color = "black",
                                        y = mean_correct)) +
    facet_grid(cols = vars(age_group)) +
    geom_boxplot(alpha = .5, color = "black") +
   # geom_errorbar(aes(ymin = group_mean_correct - se_correct, ymax = group_mean_correct + se_correct), 
  #                width = .1) + 
    xlab("Stimulus Repetition") +
    ylab("Proportion of Correct Responses") +
    scale_fill_manual(values = c(color1, color2),
                       name = "Block Condition") + 
    geom_hline(yintercept = .5, linetype = "dashed") +
    scale_y_continuous(breaks = c(.5, .7, .9)) +
    mem_theme +
    theme(legend.position = "top")
correct_response_plot
```

```{r plot learning by age group lines}

#plot
learning_lines_plot <- ggplot() +
    facet_grid(cols = vars(age_group)) +
       geom_point(
        data = correct_response_summary_sub,
        aes(x = factor(stimulus_repetition), color = reward_condition, y = mean_correct),
        shape = 95,
        size = 10,
        alpha = .2
    ) +
    geom_point(
        data = correct_response_summary,
        aes(x = factor(stimulus_repetition), 
            y = group_mean_correct,
            color = reward_condition),
        size = 2
    ) +
    geom_errorbar(
        data = correct_response_summary,
        aes(
            x = factor(stimulus_repetition),
            y = group_mean_correct,
            color = reward_condition,
            ymin = group_mean_correct - se_correct,
            ymax = group_mean_correct + se_correct),
        width = .1
    ) +
    geom_line(
        data = correct_response_summary,
        aes(x = factor(stimulus_repetition), 
            y = group_mean_correct,
            color = reward_condition, 
            group = reward_condition),
        linewidth = 1
    ) +
    xlab("Stimulus Repetition") +
    ylab("Proportion of Correct Responses") +
        scale_color_manual(values = c(color1, color2),
                       name = "Block Condition") + 
    geom_hline(yintercept = .5, linetype = "dashed") +
    mem_theme  +
    theme(legend.position = "top")
learning_lines_plot
```


## Supplementary Figure: Correct response by block condition and block number
```{r plot learning by block number}

# Plot correct response as a function of reward condition and stimulus repetition 
correct_response_summary_sub <- learning_data %>%
    filter(block_condition == "2" | cat_type != "neutral") %>%
    filter(rt > 0) %>%
    group_by(within_condition_block_num, reward_condition, subject_id,) %>%
    summarize(mean_correct = mean(correct_response_made, na.rm = T))

correct_response_summary <- correct_response_summary_sub  %>%
    group_by(within_condition_block_num, reward_condition) %>%
    summarize(group_mean_correct = mean(mean_correct, na.rm = T),
              se_correct = se(mean_correct))

#group means
correct_response_plot <- ggplot(correct_response_summary_sub, 
                                    aes(x = factor(within_condition_block_num), 
                                        fill = reward_condition,
                                        y = mean_correct)) +
    geom_boxplot(alpha = .5) + 
    xlab("Block Number") +
    ylab("Proportion of Correct Responses") +
    scale_fill_manual(values = c(color1, color2),
                       name = "Block Condition") +
    geom_hline(yintercept = .5, linetype = "dashed") +
    mem_theme +
    theme(legend.position = "none")
correct_response_plot
```


```{r plot learning by block number lines}

# Plot correct response as a function of reward condition and stimulus repetition 
correct_response_summary_sub <- learning_data %>%
    filter(block_condition == "2" | cat_type != "neutral") %>%
    filter(rt > 0) %>%
    group_by(stimulus_repetition, within_condition_block_num, reward_condition, subject_id,) %>%
    summarize(mean_correct = mean(correct_response_made, na.rm = T))

correct_response_summary <- correct_response_summary_sub  %>%
    group_by(stimulus_repetition, within_condition_block_num, reward_condition) %>%
    summarize(group_mean_correct = mean(mean_correct, na.rm = T),
              se_correct = se(mean_correct))

#plot
learning_lines_plot <- ggplot() +
    facet_grid(cols = vars(within_condition_block_num)) +
       geom_point(
        data = correct_response_summary_sub,
        aes(x = factor(stimulus_repetition), color = reward_condition, y = mean_correct),
        shape = 95,
        size = 10,
        alpha = .2
    ) +
    geom_point(
        data = correct_response_summary,
        aes(x = factor(stimulus_repetition), 
            y = group_mean_correct,
            color = reward_condition),
        size = 2
    ) +
    geom_errorbar(
        data = correct_response_summary,
        aes(
            x = factor(stimulus_repetition),
            y = group_mean_correct,
            color = reward_condition,
            ymin = group_mean_correct - se_correct,
            ymax = group_mean_correct + se_correct),
        width = .1
    ) +
    geom_line(
        data = correct_response_summary,
        aes(x = factor(stimulus_repetition), 
            y = group_mean_correct,
            color = reward_condition, 
            group = reward_condition),
        linewidth = 1
    ) +
    xlab("Stimulus Repetition") +
    ylab("Proportion of Correct Responses") +
        scale_color_manual(values = c(color1, color2),
                       name = "Block Condition") + 
    geom_hline(yintercept = .5, linetype = "dashed") +
    mem_theme  +
    theme(legend.position = "top")
learning_lines_plot
```


## Figure 2B: Generalization by block condition, category repetition, age group
```{r generalization data processing}

# add category to learning data frame
learning_data <- learning_data %>%
    separate(stimulus,
             into = c(NA, "image"),
             sep = "/") %>%
    mutate(stim_num = parse_number(image)) %>%
    separate(image,
             into = c("category", NA),
             sep = "([12345678])",
             remove=FALSE)

# determine category repetition number
learning_data <- learning_data %>%
    group_by(subject_id, task_block, category, age_group) %>%
    mutate(category_rep = rank(trial_index))
```


```{r plot generalization by age group lines}

# determine correct responses as a function of stimulus rep and category rep
correct_response_category_rep_sub <- learning_data %>%
    filter(block_condition == "2" | cat_type != "neutral") %>%
    filter(rt > 0) %>%
    mutate(category_rep_group = case_when(category_rep < 6 ~ "1 - 5",
                                          category_rep > 5 & category_rep < 12 ~ "6 - 11",
                                          category_rep > 11 ~ "12 - 17")) %>%
    group_by(reward_condition, stimulus_repetition, category_rep_group, age_group, subject_id) %>%
    summarize(mean_correct = mean(correct_response_made, na.rm = T))  %>%
    filter(stimulus_repetition == 1)

correct_response_category_rep_sub$category_rep_group <- factor(correct_response_category_rep_sub$category_rep_group, levels = c("1 - 5", "6 - 11", "12 - 17"))

correct_response_category_rep <- correct_response_category_rep_sub %>%
    group_by(reward_condition, stimulus_repetition, category_rep_group, age_group) %>%
    summarize(mean_correct_group = mean(mean_correct, na.rm = T),
              se_correct = sd(mean_correct, na.rm = T)/sqrt(n()))  %>%
    filter(stimulus_repetition == 1)

#plot
correct_response_category_rep_plot <- ggplot() +
    facet_grid(cols = vars(age_group)) +
       geom_point(
        data = correct_response_category_rep_sub,
        aes(x = category_rep_group, color = reward_condition, y = mean_correct),
        shape = 95,
        size = 15,
        alpha = .2
    ) +
    geom_point(
        data = correct_response_category_rep,
        aes(x = category_rep_group, y = mean_correct_group,
        color = reward_condition),
        size = 2
    ) +
    geom_errorbar(
        data = correct_response_category_rep,
        aes(
            x = category_rep_group,
            y = mean_correct_group,
            color = reward_condition,
            ymin = mean_correct_group - se_correct,
            ymax = mean_correct_group + se_correct),
        width = .1
    ) +
    geom_line(
        data = correct_response_category_rep,
        aes(x = category_rep_group, y = mean_correct_group,
        color = reward_condition, group = reward_condition),
        linewidth = 1
    ) +
    xlab("Category Repetition") +
    ylab("Correct Responses to 1st Stim.") +
        scale_color_manual(values = c(color1, color2),
                       name = "Block Condition") + 
    geom_hline(yintercept = .5, linetype = "dashed") +
    mem_theme  +
    theme(legend.position = "top",
          axis.text.x = element_text(angle = 52, hjust = 1))
correct_response_category_rep_plot
```


```{r plot generalization by age group boxplot}


#plot
correct_response_category_rep_plot <- ggplot() +
    facet_grid(cols = vars(age_group)) +
       geom_boxplot(
        data = correct_response_category_rep_sub,
        aes(x = category_rep_group, fill = reward_condition, y = mean_correct),
        alpha = .5
    ) +
    xlab("Category Repetition") +
    ylab("Correct Responses to 1st Stim.") +
        scale_fill_manual(values = c(color1, color2),
                       name = "Block Condition") + 
    geom_hline(yintercept = .5, linetype = "dashed") +
    mem_theme  +
    theme(legend.position = "top",
          axis.text.x = element_text(angle = 52, hjust = 1),
          legend.title = element_text(face = "plain"))
correct_response_category_rep_plot
```

## Model: Correct response to first appearance of each stimulus
```{r fit generalization model}
cr_first_rep_data  <- learning_data %>%
    filter(block_condition == "2" | cat_type != "neutral") %>%
    filter(rt > 0) %>%
    select(correct_response_made, age, category_rep, reward_condition, within_condition_block_num, subject_id, stimulus_repetition) %>%
    filter(stimulus_repetition == 1) %>%
    drop_na()

#scale variables
cr_first_rep_data$age_scaled <- scale_this(cr_first_rep_data$age)
cr_first_rep_data$category_rep_scaled <- scale_this(cr_first_rep_data$category_rep)
cr_first_rep_data$block_number_scaled <- scale_this(cr_first_rep_data$within_condition_block_num)

#run model
cr_first_rep_model <- mixed(correct_response_made ~ age_scaled * category_rep_scaled * reward_condition * block_number_scaled + (block_number_scaled * reward_condition || subject_id),
                           data = cr_first_rep_data,
                           family = "binomial",
                           method = "LRT",
                           expand_re = T,
                           control = glmerControl(optimizer = "bobyqa"))
nice(cr_first_rep_model)

# with full random effects: singular fit
# removed interactions between random slope: still singular fit
# removed block number random slope: still singular fit
# removed category rep random slope, put block number and interaction back in: converges

# Significant effects of:
# age
# category rep
# block condition
# block number
# age x category rep
# age x block condition
# category rep x block condition
# category rep x block number
# block condition x block number
# age x category rep x block condition
# category rep x block condition x block number
```

```{r display generalization model}
cr_first_rep_model.glmer <- mixed(correct_response_made ~ age_scaled * category_rep_scaled * reward_condition * block_number_scaled + (block_number_scaled * reward_condition || subject_id),
                           data = cr_first_rep_data,
                           family = "binomial",
                           method = "LRT",
                           expand_re = T,
                           control = glmerControl(optimizer = "bobyqa"),
                           return = "merMod")

tab_model_glmer(cr_first_rep_model.glmer)
```

## Supplementary Figure: Generalization by trial, reward condition, and block number
```{r plot generalization by block number}

# determine correct responses as a function of stimulus rep and category rep
correct_response_category_rep_sub <- learning_data %>%
    filter(block_condition == "2" | cat_type != "neutral") %>%
    filter(rt > 0) %>%
    mutate(category_rep_group = case_when(category_rep < 6 ~ "1 - 5",
                                          category_rep > 5 & category_rep < 12 ~ "6 - 11",
                                          category_rep > 11 ~ "12 - 17")) %>%
    group_by(reward_condition, stimulus_repetition, category_rep_group, within_condition_block_num, subject_id) %>%
    summarize(mean_correct = mean(correct_response_made, na.rm = T))  %>%
    filter(stimulus_repetition == 1)

correct_response_category_rep_sub$category_rep_group <- factor(correct_response_category_rep_sub$category_rep_group, levels = c("1 - 5", "6 - 11", "12 - 17"))

correct_response_category_rep <- correct_response_category_rep_sub %>%
    group_by(reward_condition, stimulus_repetition, category_rep_group, within_condition_block_num) %>%
    summarize(mean_correct_group = mean(mean_correct, na.rm = T),
              se_correct = sd(mean_correct, na.rm = T)/sqrt(n()))  %>%
    filter(stimulus_repetition == 1)

#plot
correct_response_category_rep_plot <- ggplot() +
    facet_grid(cols = vars(within_condition_block_num)) +
       geom_point(
        data = correct_response_category_rep_sub,
        aes(x = category_rep_group, color = reward_condition, y = mean_correct),
        shape = 95,
        size = 15,
        alpha = .05
    ) +
    geom_point(
        data = correct_response_category_rep,
        aes(x = category_rep_group, y = mean_correct_group,
        color = reward_condition),
        size = 2
    ) +
    geom_errorbar(
        data = correct_response_category_rep,
        aes(
            x = category_rep_group,
            y = mean_correct_group,
            color = reward_condition,
            ymin = mean_correct_group - se_correct,
            ymax = mean_correct_group + se_correct),
        width = .1
    ) +
    geom_line(
        data = correct_response_category_rep,
        aes(x = category_rep_group, y = mean_correct_group,
        color = reward_condition, group = reward_condition),
        linewidth = 1
    ) +
    xlab("Category Repetition") +
    ylab("Correct Responses to 1st Stim.") +
        scale_color_manual(values = c(color1, color2),
                       name = "Block Condition") + 
    geom_hline(yintercept = .5, linetype = "dashed") +
    mem_theme  +
    theme(legend.position = "top",
          axis.text.x = element_text(angle = 52, hjust = 1))
correct_response_category_rep_plot
```

## Figure 2C: WSLS by age group
```{r plot WSLS by age group}

#first determine prior response and prior reward to previous category appearance
learning_data <- learning_data %>% 
    group_by(subject_id, block_order, category) %>%
    mutate(prior_cat_stim = lag(image), #previous stimulus
           prior_cat_response = lag(key_press), #previous response
           prior_cat_reward = lag(approach_reward),
           prior_cat_correct_response_made = lag(correct_response_made), #previous outcome (win or lose) 
           category_stay = case_when(prior_cat_response == key_press ~ 1,
                                prior_cat_response != key_press ~ 0),
           same_stim = case_when(image == prior_cat_stim ~ 1,
                                 image != prior_cat_stim ~ 0)) %>%
    ungroup() %>%
        mutate(WSLS = case_when(prior_cat_correct_response_made == 1 & category_stay == 1 ~ 1, #win-stay
                            prior_cat_correct_response_made == 1 & category_stay == 0 ~ 0, #win-shift
                            prior_cat_correct_response_made == 0 & category_stay == 1 ~ 0, #lose-shift
                            prior_cat_correct_response_made == 0 & category_stay == 0 ~ 1)) #lose-stay

#determine win-stay lose shift behavior across age group and blocks
win_stay_lose_shift <- learning_data %>%
    filter(same_stim == 0) %>% #different stim only
    mutate(trial_group = ntile(learning_trial, 3)) %>%
    group_by(subject_id, age, age_group, reward_condition, trial_group) %>%
    summarize(mean_WSLS = mean(WSLS, na.rm = T),
              se_WSLS = se(WSLS)) %>%
    drop_na()

#plot
WSLS_plot <- ggplot(win_stay_lose_shift, aes(x = trial_group, y = mean_WSLS, fill = reward_condition), alpha = .5) +
    facet_grid(cols = vars(age_group)) +
    geom_boxplot(data = filter(win_stay_lose_shift, trial_group == 1), alpha = .5) + 
    geom_boxplot(data = filter(win_stay_lose_shift, trial_group == 2), alpha = .5) +
    geom_boxplot(data = filter(win_stay_lose_shift, trial_group == 3), alpha = .5) +
    scale_fill_manual(values = c(color1, color2),
                      name = "Block Condition") + 
    geom_hline(yintercept = .5, linetype = "dashed") +
    xlab("Trial Group (17 trials)") +
    ylab("Category Win-Stay Lose-Shift") +
    scale_x_continuous(breaks = c(1, 2, 3), labels = c(1, 2, 3)) +
    coord_cartesian(ylim = c(.3, 1)) +
    mem_theme  +
    theme(legend.position = "top")
WSLS_plot 
```


```{r plot WSLS by age group lines}

win_stay_lose_shift_group <- win_stay_lose_shift %>%
    group_by(age_group, reward_condition, trial_group) %>%
    summarize(group_mean_WSLS = mean(mean_WSLS, na.rm = T),
              se_WSLS = se(mean_WSLS)) %>%
    drop_na()

#plot
wsls_lines_plot <- ggplot() +
    facet_grid(cols = vars(age_group)) +
       geom_point(
        data = win_stay_lose_shift,
        aes(x = factor(trial_group), color = reward_condition, y = mean_WSLS),
        shape = 95,
        size = 15,
        alpha = .2
    ) +
    geom_point(
        data = win_stay_lose_shift_group,
        aes(x = factor(trial_group), 
            y = group_mean_WSLS,
            color = reward_condition),
        size = 2
    ) +
    geom_errorbar(
        data = win_stay_lose_shift_group,
        aes(
            x = factor(trial_group),
            y = group_mean_WSLS,
            color = reward_condition,
            ymin = group_mean_WSLS - se_WSLS,
            ymax = group_mean_WSLS + se_WSLS),
        width = .1
    ) +
    geom_line(
        data = win_stay_lose_shift_group,
        aes(x = factor(trial_group), 
            y = group_mean_WSLS,
            color = reward_condition, 
            group = reward_condition),
        linewidth = 1
    ) +
    xlab("Trial Group (17 Trials)") +
    ylab("Category Win-Stay-Lose-Shift") +
        scale_color_manual(values = c(color1, color2),
                       name = "Block Condition") + 
    geom_hline(yintercept = .5, linetype = "dashed") +
    mem_theme  +
    theme(legend.position = "top")
wsls_lines_plot
```

## Supplementary Figure: WSLS by block number
```{r WSLS plot with block number}

#determine win-stay lose shift behavior across age group and blocks
win_stay_lose_shift <- learning_data %>%
    filter(same_stim == 0) %>% #different stim only
    mutate(trial_group = floor(learning_trial/17 + 50/51)) %>%
    group_by(subject_id, age, age_group, reward_condition, trial_group, within_condition_block_num) %>%
    summarize(mean_WSLS = mean(WSLS, na.rm = T),
              se_WSLS = se(WSLS)) %>%
    drop_na()

#plot
WSLS_plot <- ggplot(win_stay_lose_shift, aes(x = factor(within_condition_block_num), y = mean_WSLS, fill = reward_condition)) +
    geom_boxplot(alpha = .5) + 
    scale_fill_manual(values = c(color1, color2),
                      name = "Block Condition") + 
    scale_color_manual(values = c(color1, color2),
                      name = "Block Condition") + 
    geom_hline(yintercept = .5, linetype = "dashed") +
    xlab("Block Number") +
    ylab("Category WSLS") +
    mem_theme + 
    theme(legend.position = "none")
WSLS_plot 
```

```{r plot WSLS by block number lines}

win_stay_lose_shift_group <- win_stay_lose_shift %>%
    group_by(within_condition_block_num, reward_condition, trial_group) %>%
    summarize(group_mean_WSLS = mean(mean_WSLS, na.rm = T),
              se_WSLS = se(mean_WSLS)) %>%
    drop_na()

#plot
wsls_lines_plot <- ggplot() +
    facet_grid(cols = vars(within_condition_block_num)) +
       geom_point(
        data = win_stay_lose_shift,
        aes(x = factor(trial_group), color = reward_condition, y = mean_WSLS),
        shape = 95,
        size = 15,
        alpha = .2
    ) +
    geom_point(
        data = win_stay_lose_shift_group,
        aes(x = factor(trial_group), 
            y = group_mean_WSLS,
            color = reward_condition),
        size = 2
    ) +
    geom_errorbar(
        data = win_stay_lose_shift_group,
        aes(
            x = factor(trial_group),
            y = group_mean_WSLS,
            color = reward_condition,
            ymin = group_mean_WSLS - se_WSLS,
            ymax = group_mean_WSLS + se_WSLS),
        width = .1
    ) +
    geom_line(
        data = win_stay_lose_shift_group,
        aes(x = factor(trial_group), 
            y = group_mean_WSLS,
            color = reward_condition, 
            group = reward_condition),
        linewidth = 1
    ) +
    xlab("Trial Group (17 Trials)") +
    ylab("Category Win-Stay-Lose-Shift") +
        scale_color_manual(values = c(color1, color2),
                       name = "Block Condition") + 
    geom_hline(yintercept = .5, linetype = "dashed") +
    mem_theme  +
    theme(legend.position = "top")
wsls_lines_plot
```

## Supplementary Figure: WSLS by block number and age group
```{r WSLS plot with block number and age group, fig.height = 10}

#plot
WSLS_plot <- ggplot(win_stay_lose_shift, aes(x = factor(trial_group), y = mean_WSLS, fill = reward_condition)) +
    facet_wrap(~age_group * factor(within_condition_block_num)) +
    geom_boxplot(alpha = .5) + 
    scale_fill_manual(values = c(color1, color2),
                      name = "Block Condition") + 
    scale_color_manual(values = c(color1, color2),
                      name = "Block Condition") + 
    geom_hline(yintercept = .5, linetype = "dashed") +
    xlab("Trial Group") +
    ylab("Category WSLS") +
    mem_theme + 
    theme(legend.position = "none")
WSLS_plot 
```

## Model: Category win-stay lose-shift
```{r fit WSLS model}

#determine win-stay lose shift behavior across age group and blocks
wsls_model_data <- learning_data %>% 
    filter(rt > 0) %>%
    filter(same_stim == 0) %>% #different stim only
    mutate(WSLS = case_when(prior_cat_correct_response_made == 1 & category_stay == 1 ~ 1, 
                            prior_cat_correct_response_made == 1 & category_stay == 0 ~ 0,
                            prior_cat_correct_response_made == 0 & category_stay == 1 ~ 0, 
                            prior_cat_correct_response_made == 0 & category_stay == 0 ~ 1)) %>%
    select(subject_id, age, WSLS, learning_trial, reward_condition, block_order, within_condition_block_num) %>%
    drop_na() 

#scale variables
wsls_model_data$age_scaled <- scale_this(wsls_model_data$age)
wsls_model_data$learning_trial_scaled <- scale_this(wsls_model_data$learning_trial)
wsls_model_data$block_number_scaled <- scale_this(wsls_model_data$within_condition_block_num)

#run model 
wsls_model <- mixed(WSLS ~ age_scaled * learning_trial_scaled * reward_condition * block_number_scaled  + (reward_condition + block_number_scaled || subject_id),
                    data = wsls_model_data,
                    family = "binomial",
                    method = "LRT",
                    expand_re = T,
                    control = glmerControl(optimizer = "bobyqa"))
nice(wsls_model)

# with full random effects: singular fit
# removed interactions between random slopes - still singular fit 
# removed trial number random slope

# significant effects of:
# age
# block condition
# block number
# age x block condition
# trial x block condition
# block condition x block number
# age x trial x block condition
```

```{r display WSLS model}
wsls_model.glmer <- mixed(WSLS ~ age_scaled * learning_trial_scaled * reward_condition * block_number_scaled  + (reward_condition + block_number_scaled || subject_id),
                    data = wsls_model_data,
                    family = "binomial",
                    method = "LRT",
                    expand_re = T,
                    control = glmerControl(optimizer = "bobyqa"),
                    return = "merMod")
                    
tab_model_glmer(wsls_model.glmer)
```

## Stats: WSLS in first 10 trials
```{r WSLS means in first 10 trials}
win_stay_lose_shift_first10_means <- learning_data %>%
    filter(rt > 0) %>% #responses only
    filter(same_stim == 0) %>% #different stim only
    mutate(WSLS = case_when(prior_cat_correct_response_made == 1 & category_stay == 1 ~ 1, 
                            prior_cat_correct_response_made == 1 & category_stay == 0 ~ 0,
                            prior_cat_correct_response_made == 0 & category_stay == 1 ~ 0, 
                            prior_cat_correct_response_made == 0 & category_stay == 0 ~ 1)) %>%
    group_by(subject_id, age_group, reward_condition, prior_cat_correct_response_made) %>%
    filter(learning_trial < 10) %>%
    group_by(reward_condition) %>%
    summarize(mean_WSLS = mean(WSLS, na.rm = T),
              se_WSLS = se(WSLS)) %>%
    drop_na()

pander(win_stay_lose_shift_first10_means)
```


## Supplementary Model: Influence of prior category and exemplar rewards on choice 
```{r prior rewards model}

#format data
prior_reward_model_data <-  learning_data %>%
    filter(rt > 0) %>%
    group_by(subject_id, image) %>%
    mutate(prior_stim_response = lag(key_press), #previous response
           prior_stim_reward = lag(approach_reward),
           prior_stim_reward = replace_na(prior_stim_reward, 0)
           ) %>%
    ungroup() %>%
    mutate(choice = as.numeric(key_press),
           prior_cat_reward = as.numeric(str_extract(prior_cat_reward, "-?\\d+")),
           prior_cat_reward = replace_na(prior_cat_reward, 0),
           prior_cat_diff_stim_reward = case_when(same_stim == 1 ~ 0,
                                                  same_stim == 0 ~ prior_cat_reward),
           prior_cat_diff_stim_reward = replace_na(prior_cat_diff_stim_reward, 0)) %>%
    select(subject_id, age, learning_trial, reward_condition, within_condition_block_num, prior_cat_diff_stim_reward, prior_cat_reward, prior_stim_reward, choice, key_press) %>%
    filter(choice %in% c(0, 1))

#scale variables
prior_reward_model_data$age_scaled <- scale_this(prior_reward_model_data$age)
prior_reward_model_data$learning_trial_scaled <- scale_this(prior_reward_model_data$learning_trial)
prior_reward_model_data$block_number_scaled <- scale_this(prior_reward_model_data$within_condition_block_num)
prior_reward_model_data$prior_cat_reward_scaled <- scale_this(prior_reward_model_data$prior_cat_reward)
prior_reward_model_data$prior_cat_diff_stim_reward_scaled <- scale_this(prior_reward_model_data$prior_cat_diff_stim_reward)
prior_reward_model_data$prior_stim_reward_scaled <- scale_this(prior_reward_model_data$prior_stim_reward)

#run model
prior_reward_model <- mixed(choice ~ (prior_cat_reward_scaled + prior_stim_reward_scaled) * reward_condition * learning_trial_scaled * age_scaled  + (prior_cat_reward_scaled + prior_stim_reward_scaled + reward_condition + learning_trial_scaled || subject_id),
                    data = prior_reward_model_data,
                    family = "binomial",
                    method = "LRT",
                    expand_re = T,
                    control = glmerControl(optimizer = "bobyqa"))
nice(prior_reward_model)

#note: is singular with interactions in RE

```

```{r display prior rewards model}
prior_reward_model.glmer <- mixed(choice ~ (prior_cat_reward_scaled + prior_stim_reward_scaled) * reward_condition * learning_trial_scaled * age_scaled  + ((prior_cat_reward_scaled + prior_stim_reward_scaled) * reward_condition * learning_trial_scaled || subject_id),
                    data = prior_reward_model_data,
                    family = "binomial",
                    method = "LRT",
                    expand_re = T,
                    control = glmerControl(optimizer = "bobyqa"),
                    return = "merMod")
                    
tab_model_glmer(prior_reward_model.glmer)
```

## Supplementary Figure: Influence of prior category and exemplar rewards on choice 
```{r sjplot prior exemplar model}

sjPlot::set_theme( 
    base = theme_classic(),
    legend.item.backcol = "transparent",
    geom.boxoutline.color = "black",
    axis.textsize = 1,
    axis.textcolor = "black",
    axis.title.color = "black",
    axis.title.size = 1.1,
    axis.title.x.vjust = -.25,
    axis.title.y.vjust = 1,
    legend.title.size = 1.05)

plot_model(prior_reward_model.glmer, type = "pred",
           terms = c("learning_trial_scaled", "prior_stim_reward_scaled", "reward_condition"),
           colors = c("#FFCA4B", "#6364a5", "#45b5aa")) +
    scale_color_manual(values = c(color1, color2, color3), name = "Prior Same Exemplar Reward",
                       labels = c("~ negative",
                                  "~ 0",
                                  "~ positive"
                                  )) +
    scale_fill_manual(values = c(color1, color2, color3), name = "Prior Same Exemplar Reward",
                       labels = c("~ negative",
                                  "~ 0",
                                  "~ positive"
                                  )) +
    xlab("Learning Trial (Scaled)") +
    ylab('p(Approach)')

plot_model(prior_reward_model.glmer, type = "pred",
           terms = c("learning_trial_scaled", "prior_cat_reward_scaled", "reward_condition"),
           colors = c("#FFCA4B", "#6364a5", "#45b5aa")) +
    scale_color_manual(values = c(color1, color2, color3), name = "Prior Same Category Reward",
                       labels = c("~ negative",
                                  "~ 0",
                                  "~ positive"
                                  )) +
    scale_fill_manual(values = c(color1, color2, color3), name = "Prior Same Category Reward",
                       labels = c("~ negative",
                                  "~ 0",
                                  "~ positive"
                                  )) +
    xlab("Learning Trial (Scaled)") +
    ylab('p(Approach)')


plot_model(prior_reward_model.glmer, type = "pred",
           terms = c("age_scaled", "prior_stim_reward_scaled", "reward_condition"),
           colors = c("#FFCA4B", "#6364a5", "#45b5aa")) +
    scale_color_manual(values = c(color1, color2, color3), name = "Prior Same Exemplar Reward",
                       labels = c("~ negative",
                                  "~ 0",
                                  "~ positive"
                                  )) +
    scale_fill_manual(values = c(color1, color2, color3), name = "Prior Same Exemplar Reward",
                       labels = c("~ negative",
                                  "~ 0",
                                  "~ positive"
                                  )) +
    xlab("Age (Scaled)") +
    ylab('p(Approach)') 

plot_model(prior_reward_model.glmer, type = "pred",
           terms = c("age_scaled", "prior_cat_reward_scaled", "reward_condition"),
           colors = c("#FFCA4B", "#6364a5", "#45b5aa")) +
    scale_color_manual(values = c(color1, color2, color3), name = "Prior Same Category Reward",
                       labels = c("~ negative",
                                  "~ 0",
                                  "~ positive"
                                  )) +
    scale_fill_manual(values = c(color1, color2, color3), name = "Prior Same Category Reward",
                       labels = c("~ negative",
                                  "~ 0",
                                  "~ positive"
                                  )) +
    xlab("Age (Scaled)") +
    ylab('p(Approach)') 
```


# Memory
```{r import and format memory data}

#combine and process
memory_data <-  read_csv('data/e1_memory_data.csv') %>%
    filter(task_block != "practice") %>%
    filter(is.na(mem_acc) == F)

#relabel foil type and reward condition
memory_data$foil_type <- factor(memory_data$foil_type, levels = c("old", "exemplar", "category"),
                                  labels = c("Old", "Novel Exemplar", "Novel Category"))

memory_data$reward_condition <- factor(memory_data$block_condition,
                                            levels = c(1, 2),
                                            labels = c("Category-Predictive", "Exemplar-Predictive"))

#combine with subject ages
memory_data <- inner_join(memory_data, subject_list, by = c("subject_id"))
```

## Overall descriptive memory stats
```{r memory stats}

memory_sub_means <- memory_data %>%
    group_by(subject_id, age_group) %>%
    summarize(mean_sub_mem = mean(mem_acc, na.rm = T))

memory_group_mean <- memory_sub_means %>%
    summarize(mean_mem = mean(mean_sub_mem, na.rm = T),
              se_mem = se(mean_sub_mem))

memory_agegroup_mean <- memory_sub_means %>%
    group_by(age_group) %>%
    summarize(mean_mem = mean(mean_sub_mem, na.rm = T),
              se_mem = se(mean_sub_mem))

pander(memory_group_mean)
pander(memory_agegroup_mean)
```

## Memory delay stats
```{r memory delay stats}
mem_delay_overall_data <- memory_data %>%
    select(subject_id, age_group, memory_delay) %>%
    unique() %>%
    summarize(mean_delay = mean(memory_delay, na.rm = T),
              sd_delay = sd(memory_delay, na.rm = T),
              min_delay = min(memory_delay, na.rm = T),
              max_delay = max(memory_delay, na.rm = T))
pander(mem_delay_overall_data)

mem_delay_dist <- memory_data %>%
    select(subject_id, age_group, memory_delay) %>%
    unique() %>%
    group_by(memory_delay) %>%
    summarize(n = n()) %>%
    drop_na()
pander(mem_delay_dist)
```

## Supplementary Figure: AUC values by stimulus repetitions, block condition, age group
```{r data processing for plotting memory AUC by stimulus repetition}
one_rep_AUCs <- memory_data %>%
    filter(num_stim_rep %in% c(NA, 1)) %>%
    select(subject_id, memory_delay, age_group, reward_condition, correct_mem_response, conf_rating, num_stim_rep) %>%
    group_by(subject_id, memory_delay, age_group, reward_condition) %>%
    mutate(one_rep = as.numeric(roc(correct_mem_response ~ conf_rating)$auc)) %>%
    select(subject_id, memory_delay, reward_condition, one_rep) %>%
    unique()

three_rep_AUCs <- memory_data %>%
    filter(num_stim_rep %in% c(NA, 3)) %>%
    select(subject_id, memory_delay, age_group, reward_condition, correct_mem_response, conf_rating, num_stim_rep) %>%
    group_by(subject_id, memory_delay, age_group, reward_condition) %>%
    mutate(three_rep = as.numeric(roc(correct_mem_response ~ conf_rating)$auc)) %>%
    select(subject_id, memory_delay, reward_condition, three_rep) %>%
    unique()

six_rep_AUCs <- memory_data %>%
    filter(num_stim_rep %in% c(NA, 6)) %>%
    select(subject_id, memory_delay, age_group, reward_condition, correct_mem_response, conf_rating, num_stim_rep) %>%
    group_by(subject_id, memory_delay, age_group, reward_condition) %>%
    mutate(six_rep = as.numeric(roc(correct_mem_response ~ conf_rating)$auc)) %>%
    select(subject_id, memory_delay, reward_condition, six_rep) %>%
    unique()

#combine AUCs into single data frame
stim_rep_AUCs <- full_join(one_rep_AUCs, three_rep_AUCs, by = c("subject_id", "memory_delay", "reward_condition"))
stim_rep_AUCs <- full_join(stim_rep_AUCs, six_rep_AUCs, by = c("subject_id", "memory_delay", "reward_condition")) %>%
    pivot_longer(cols = c(one_rep, three_rep, six_rep),
                 names_to = "stimulus_reps",
                 values_to = "AUC")

stim_rep_AUCs$stimulus_reps <- factor(stim_rep_AUCs$stimulus_reps,
                                      levels = c("one_rep", "three_rep", "six_rep"),
                                      labels = c(1, 3, 6))
```

```{r plot auc by stim rep}
stim_rep_auc_means <- stim_rep_AUCs %>%
    group_by(age_group, stimulus_reps, reward_condition) %>%
    summarize(mean_auc = mean(AUC, na.rm = T),
              se_auc = se(AUC))

stim_rep_auc_plot <- ggplot(stim_rep_AUCs, aes(x = stimulus_reps, fill = reward_condition, y = AUC)) +
    geom_boxplot(alpha = .5) +
    facet_grid(cols = vars(age_group)) +
    scale_fill_manual(values = c(color1, color2), name = "Block Condition") + 
    xlab("Number of Stimulus Repetitions") +
    ylab("Memory Performance (AUC)") +
    mem_theme
stim_rep_auc_plot
```

## Model: AUC values by stimulus repetitions, block condition, age
```{r fit auc by stim rep model}

stim_rep_aucs <- full_join(stim_rep_AUCs, subject_list, by = c("subject_id", "age_group")) 

#scale variables
stim_rep_aucs$age_scaled <- scale_this(stim_rep_aucs$age)
stim_rep_aucs$memory_delay_scaled <- scale_this(stim_rep_aucs$memory_delay)
stim_rep_aucs$stim_rep_scaled <- scale_this(as.numeric(as.character(stim_rep_aucs$stimulus_reps)))

#run model
stim_rep_auc_model <- mixed(AUC ~ age_scaled * reward_condition * stim_rep_scaled + (1|subject_id),
                   data = stim_rep_aucs,
                   method = "S")
nice(stim_rep_auc_model)

# effects of
# reward condition
# stimulus repetition
# age
```

```{r display auc by stim rep model}
stim_rep_auc_model.lmer <- mixed(AUC ~ age_scaled * reward_condition * stim_rep_scaled + (1|subject_id),
                   data = stim_rep_aucs,
                   method = "S",
                   return = "merMod")
                    
tab_model_glmer(stim_rep_auc_model.lmer)
```

```{r fit ROC curves for each participant and derive AUC}
exemplar_AUCs <- memory_data %>%
    filter(foil_type != "Novel Category") %>%
    select(subject_id, memory_delay, age_group, reward_condition, correct_mem_response, conf_rating) %>%
    group_by(subject_id, memory_delay, age_group, reward_condition) %>%
    mutate(exemplar = as.numeric(roc(correct_mem_response ~ conf_rating)$auc)) %>%
    select(subject_id, memory_delay, reward_condition, exemplar) %>%
    unique()

category_AUCs <- memory_data %>%
    filter(foil_type != "Novel Exemplar") %>%
    select(subject_id, memory_delay, age_group, reward_condition, correct_mem_response, conf_rating) %>%
    group_by(subject_id, memory_delay, age_group, reward_condition) %>%
    mutate(category = as.numeric(roc(correct_mem_response ~ conf_rating)$auc)) %>%
    select(subject_id, memory_delay, reward_condition, category) %>%
    unique()


#combine AUCs into single data frame
participant_AUCs <- full_join(exemplar_AUCs, category_AUCs, by = c("subject_id", "memory_delay", "age_group", "reward_condition")) %>%
    pivot_longer(cols = c(exemplar, category),
                 names_to = "foil_type",
                 values_to = "AUC")

```



## Figure 3A: AUC values by age group, memory specificity, block condition
```{r auc plot, fig.height = 7, fig.width = 4.1}
auc_overall_means <- participant_AUCs %>% 
    group_by(foil_type) %>%
    summarize(mean_auc = mean(AUC, na.rm = T),
              se_auc = se(AUC))
pander(auc_overall_means)
    
auc_means <- participant_AUCs %>%
    group_by(age_group, foil_type, reward_condition) %>%
    summarize(mean_auc = mean(AUC, na.rm = T),
              se_auc = se(AUC))


auc_plot <- ggplot(participant_AUCs) +
    facet_grid(cols = vars(age_group), rows = vars(foil_type)) +
        geom_hline(yintercept = .5, linetype = "dashed") +
       geom_point(data = participant_AUCs, aes(x = reward_condition, color = foil_type, y = AUC), shape = 95, size = 15, alpha = .2) + 
    geom_point(data = auc_means, aes(x = reward_condition, y = mean_auc), color = "black", size = 2) +
    geom_errorbar(data = auc_means, aes(x = reward_condition, y = mean_auc, ymin = mean_auc - se_auc, ymax = mean_auc + se_auc), color = "black", width = .1) +
    geom_line(data = auc_means, aes(x = reward_condition, y = mean_auc, group = age_group), color = "black", linewidth = .5) +
    scale_color_manual(values = c(color1, color2), name = "Block Condition") +
    xlab("Block Condition") +
    ylab("Memory Performance (AUC)") +
    scale_y_continuous(limits = c(.3, 1), breaks = c(.3, .5, .7, .9)) +
    mem_theme +
    theme(axis.text.x = element_text(angle = 52, hjust = 1),
          legend.position = "none")
auc_plot
```

## Model: AUCs by age, reward condition, memory specificity
```{r fit auc model}
aucs <- full_join(participant_AUCs, subject_list, by = c("subject_id", "age_group")) 

#scale variables
aucs$age_scaled <- scale_this(aucs$age)

#run model
auc_model <- mixed(AUC ~ age_scaled * reward_condition * foil_type + (1|subject_id),
                   data = aucs,
                   method = "S")
nice(auc_model)
# main effects of
# age
# reward condition
# foil type
```

```{r display auc model}
auc_model.lmer <- mixed(AUC ~ age_scaled * reward_condition * foil_type + (1|subject_id),
                   data = aucs,
                   method = "S",
                   return = "merMod")

tab_model_glmer(auc_model.lmer)
```

## Model: AUCs by age, reward condition, foil type, memory delay

```{r fit auc model with memory delay}

aucs_delay <- aucs %>%
    drop_na()

#scale variables
aucs_delay$age_scaled <- scale_this(aucs_delay$age)
aucs_delay$memory_delay_scaled <- scale_this(aucs_delay$memory_delay)


#run model
auc_delay_model <- mixed(AUC ~ age_scaled * reward_condition * foil_type * memory_delay_scaled + (1|subject_id),
                   data = aucs_delay,
                   method = "S")
nice(auc_delay_model)

# main effects of
# reward condition
# foil type
# memory delay
# age x memory delay
```

```{r display auc model with memory delay}
auc_delay_model.lmer <-  mixed(AUC ~ age_scaled * reward_condition * foil_type * memory_delay_scaled + (1|subject_id),
                   data = aucs_delay,
                   method = "S",
                   return = "merMod")

tab_model_glmer(auc_delay_model.lmer)
```

## Supplementary Figure: AUC values with delay

```{r auc plot with delay}
participant_AUCs_filtered <- participant_AUCs %>%
    drop_na() #%>%
    # filter(memory_delay > 5 & memory_delay < 10)

auc_plot <- ggplot(participant_AUCs_filtered, aes(x = as.factor(memory_delay), fill = foil_type, y = AUC)) +
    geom_boxplot(alpha = .5) +
    scale_fill_manual(values = c(color1, color2), name = "Memory Specificity") + 
    xlab("Memory Delay (Days)") +
    ylab("Memory Performance (AUC)") +
    coord_cartesian(ylim = c(.5, 1)) +
    mem_theme
auc_plot
```

# RL modeling

## Choice weights

```{r cbm parameter ests fourB_oneQ}

#read in param ests
param_ests <- read_csv("data/model_estimates/params_fourB_oneQ.csv")

#merge with age
param_ests <- full_join(param_ests, subject_list, by = c("subject_id"))
```

### Figure: Choice weights histogram

```{r beta histogram, fig.width = 7, fig.height = 5}

#pivot longer
beta_ests <- param_ests %>%
    pivot_longer(cols = c(beta_c_cCond: beta_e_eCond),
                 names_to = "beta_parameter",
                 names_prefix = "beta_",
                 values_to = "est") %>%
    separate(beta_parameter, into = c("beta_val", "block_condition"), sep = "_") %>%
    drop_na()

beta_ests$abstraction <- factor(beta_ests$beta_val,
                                levels = c("c", "e"),
                                labels = c("category", "exemplar"))

beta_ests$reward_condition <- factor(beta_ests$block_condition,
                                levels = c("cCond", "eCond"),
                                labels = c("Category-Predictive", "Exemplar-Predictive"))

#find means to add to plot
beta_means <- beta_ests %>%
    group_by(reward_condition, abstraction, age_group) %>%
    summarize(mean_est = mean(est, na.rm = T),
              se_est = se(est))

#plot
beta_histogram <- ggplot(beta_ests, aes(x = est)) +
    facet_grid(rows = vars(abstraction), cols = vars(age_group)) + 
    geom_histogram(position = "identity", color = 'black', aes(fill = reward_condition), alpha = .5) +
    geom_vline(data = beta_means, aes(xintercept = mean_est, color = reward_condition), linewidth = 2) + 
    xlab("Choice Weight Magnitude") +
    ylab("Number of Participants") +
    scale_y_continuous(breaks = c(0, 3, 6, 9)) +
    scale_fill_manual(values = c(color1, color2), name = "Block Condition") +
    scale_color_manual(values = c(color1, color2), name = "Block Condition") +
    mem_theme +
    theme(legend.position = "top")
beta_histogram
```

### Figure 2E: Choice weights boxplots
```{r simple choice weights fig}

#plot
choice_weights_plot <- ggplot(beta_ests, aes(y = est, x = abstraction, fill = reward_condition)) +
    facet_grid(cols = vars(age_group)) + 
    geom_boxplot(alpha = .5) +
    xlab("Choice Weight Magnitude") +
    ylab("Estimate") +
    scale_fill_manual(values = c(color1, color2), name = "Block Condition") +
    mem_theme +
    theme(legend.position = "top", 
          legend.text = element_text(face = "plain"),
          legend.title = element_text(face = "plain"))
choice_weights_plot
```

```{r choice weights lines fig, fig.height = 6}

#plot
choice_weights_lines_plot <- ggplot() +
    facet_grid(cols = vars(age_group)) +
       geom_point(
        data = beta_ests,
        aes(x = reward_condition, color = abstraction, y = est),
        shape = 95,
        size = 15,
        alpha = .2
    ) +
    geom_point(
        data = beta_means,
        aes(x = reward_condition, 
            y = mean_est,
            color = abstraction),
        size = 2
    ) +
    geom_errorbar(
        data = beta_means,
        aes(
            x = reward_condition,
            y = mean_est,
            color = abstraction,
            ymin = mean_est - se_est,
            ymax = mean_est + se_est),
        width = .1
    ) +
    geom_line(
        data = beta_means,
        aes(x = reward_condition, 
            y = mean_est,
            color = abstraction, 
            group = abstraction),
        linewidth = 1
    ) +
    xlab("Block Condition") +
    ylab("Estimate") +
        scale_color_manual(values = c(color1, color2),
                       name = "Choice Weight") + 
    mem_theme  +
    theme(legend.position = "top",
          axis.text.x = element_text(angle = 52, hjust = 1))
choice_weights_lines_plot
```

### Presentation figure: Choice weights without age
```{r simple choice weights fig no age}

#plot
choice_weights_plot_no_age <- ggplot(beta_ests, aes(y = est, x = abstraction, fill = reward_condition)) +
    geom_boxplot() +
    xlab("Choice Weight") +
    ylab("Estimate") +
    scale_fill_manual(values = c(color1, color2), name = "Block Condition") +
    mem_theme +
    theme(legend.position = "right")
choice_weights_plot_no_age
```

### Model: Choice weights by block condition and age
```{r fit choice weight by age model}

#scale age
beta_ests$age_scaled <- scale_this(beta_ests$age)

#do betas change across conditions and by age?
beta.age.model <- mixed(est ~ abstraction * reward_condition * age_scaled + (1|subject_id),
                            method = "S",
                           data = beta_ests)
nice(beta.age.model) 
```

```{r display choice weight by age model}
beta.age.model.lmer <- mixed(est ~ abstraction * reward_condition * age_scaled + (1|subject_id),
                            method = "S",
                           data = beta_ests,
                           return = "merMod")

tab_model_glmer(beta.age.model.lmer)
```

### Model: Exemplar choice weights across conditions
```{r fit exemplar choice weight across conditions model}

#filter and scale age
exemp_beta_ests <- beta_ests %>%
    filter(abstraction == "exemplar")

#do exemplar choice weights change across conditions?
beta.model.exemp <- mixed(est ~ reward_condition + (1|subject_id),
                            method = "S",
                           data = exemp_beta_ests)
nice(beta.model.exemp) 
```

```{r display exemplar choice weight by age model}
beta.age.model.exemp.lmer <- mixed(est ~ reward_condition + (1|subject_id),
                                   method = "S",
                                   data = exemp_beta_ests,
                                   return = "merMod")

tab_model_glmer(beta.age.model.exemp.lmer)
```

### Model: Category choice weights across conditions
```{r fit category choice weight  model}
#filter and scale age
cat_beta_ests <- beta_ests %>%
    filter(abstraction == "category")

#do betas change across conditions and by age?
beta.age.model.cat <- mixed(est ~ reward_condition + (1|subject_id),
                            method = "S",
                           data = cat_beta_ests)
nice(beta.age.model.cat) 

# reward condition
# reward condition x age interaction
```

```{r display category choice weight model}
beta.age.model.cat.lmer <- mixed(est ~ reward_condition  + (1|subject_id),
                                   method = "S",
                                   data = cat_beta_ests,
                                   return = "merMod")

tab_model_glmer(beta.age.model.cat.lmer)
```

### Supplementary Model: Relation between exemplar and category choice weights
```{r fit model looking at tradeoff between choice weights}

temp <- param_ests %>%
    pivot_longer(cols = c(beta_c_cCond, beta_c_eCond), 
                values_to = "beta_c",
                names_to = "block_condition",
                names_prefix = "beta_c_") %>%
    select(subject_id, age, age_group, block_condition, beta_c)


temp2 <- param_ests %>%
    pivot_longer(cols = c(beta_e_cCond, beta_e_eCond), 
                values_to = "beta_e",
                names_to = "block_condition",
                names_prefix = "beta_e_") %>%
    select(subject_id, block_condition, beta_e)
  
beta_ests_wide <- full_join(temp, temp2, by = c("subject_id", "block_condition"))
                

#scale continuous variables
beta_ests_wide$age_scaled <- scale_this(beta_ests_wide$age)
beta_ests_wide$beta_c_scaled <- scale_this(beta_ests_wide$beta_c)
beta_ests_wide$beta_e_scaled <- scale_this(beta_ests_wide$beta_e)

#do choice weights trade off?
beta.tradeoff.model <- mixed(beta_e_scaled ~ beta_c_scaled * age_scaled * block_condition + (1|subject_id),
                            method = "S",
                            data = beta_ests_wide)
nice(beta.tradeoff.model) 


beta.tradeoff.model.lmer <- mixed(beta_e_scaled ~ beta_c_scaled * age_scaled * block_condition + (1|subject_id),
                            method = "S",
                            data = beta_ests_wide,
                            return = "merMod")

tab_model_glmer(beta.tradeoff.model.lmer)

#main effect of age
#beta c * block condition interaction effect
```

```{r choice weight tradeoff within each block}

#filter dataset
beta_ests_wide_exemp_pred <- beta_ests_wide %>%
    filter(block_condition == "eCond")

beta_ests_wide_cat_pred <- beta_ests_wide %>%
    filter(block_condition == "cCond")

#scale continuous variables
beta_ests_wide_exemp_pred$age_scaled <- scale_this(beta_ests_wide_exemp_pred$age)
beta_ests_wide_exemp_pred$beta_c_scaled <- scale_this(beta_ests_wide_exemp_pred$beta_c)
beta_ests_wide_exemp_pred$beta_e_scaled <- scale_this(beta_ests_wide_exemp_pred$beta_e)
beta_ests_wide_cat_pred$age_scaled <- scale_this(beta_ests_wide_cat_pred$age)
beta_ests_wide_cat_pred$beta_c_scaled <- scale_this(beta_ests_wide_cat_pred$beta_c)
beta_ests_wide_cat_pred$beta_e_scaled <- scale_this(beta_ests_wide_cat_pred$beta_e)

#run models separately for each condition

#exemplar condition
beta.tradoff.model.exemp_pred <- lm(beta_e_scaled ~ beta_c_scaled * age_scaled,
                           data = beta_ests_wide_exemp_pred)
summary(beta.tradoff.model.exemp_pred)
tab_model_glmer(beta.tradoff.model.exemp_pred)

#marginal positive relation with beta_c_scaled
#positive effect of age



#category condition
beta.tradoff.model.cat_pred <- lm(beta_e_scaled ~ beta_c_scaled * age_scaled,
                           data = beta_ests_wide_cat_pred)
summary(beta.tradoff.model.cat_pred) 

#no relation with beta_c_scaled
#positive relation with age
```

### Model: Relations between choice weights and points earned
```{r choice weights points data processing}
participant_points <- learning_data %>%
    group_by(subject_id, reward_condition) %>%
    summarize(total_points = sum(points, na.rm = T)) 

#convert subject_id to factor
beta_ests$subject_id <- factor(beta_ests$subject_id)

#join
beta_ests_points <- full_join(participant_points, beta_ests, by = c("subject_id", "reward_condition"))
```

```{r fit choice weights points model}

#process data for model
beta_ests_points <- beta_ests_points %>%
    select(est, total_points, age, age_group, abstraction, reward_condition, subject_id) %>%
    drop_na()

#scale continuous variables
beta_ests_points$beta_scaled <- scale_this(beta_ests_points$est)
beta_ests_points$age_scaled <- scale_this(beta_ests_points$age)

#do beta values predict points?
beta_points_model <- mixed(total_points ~ age_scaled * beta_scaled * abstraction * reward_condition + (1|subject_id),
                           data = beta_ests_points)
nice(beta_points_model)

# effects of 
# age
# beta
# age x beta
# abstraction x block condition x beta
```

```{r fit separate regressions to look at how exemplar and category choice weights influence points across conditions}

#drop na
beta_ests_points_c_c <- beta_ests_points %>%
    filter(reward_condition == "Category-Predictive",
           abstraction == "category")

beta_ests_points_e_c <- beta_ests_points %>%
    filter(reward_condition == "Category-Predictive",
           abstraction == "exemplar")

beta_ests_points_c_e <- beta_ests_points %>%
    filter(reward_condition == "Exemplar-Predictive",
           abstraction == "category")

beta_ests_points_e_e <- beta_ests_points %>%
    filter(reward_condition == "Exemplar-Predictive",
           abstraction == "exemplar")

#do beta values predict points?
beta_points_model1 <- lm(total_points ~ est, data = beta_ests_points_c_c)
beta_points_model2 <- lm(total_points ~ est, data = beta_ests_points_e_c)
beta_points_model3 <- lm(total_points ~ est, data = beta_ests_points_c_e)
beta_points_model4 <- lm(total_points ~ est, data = beta_ests_points_e_e)

summary(beta_points_model1) #sig
tab_model_glmer(beta_points_model1)
summary(beta_points_model2) #sig
tab_model_glmer(beta_points_model2)
summary(beta_points_model3) #not sig
tab_model_glmer(beta_points_model3)
summary(beta_points_model4) #sig
tab_model_glmer(beta_points_model4)
```

### Figure 2D: Effect of choice weights on points earned
```{r points and choice weights plot, fig.height = 5}
points_beta_plot <- ggplot(beta_ests_points, aes(x = est, y = total_points, color = abstraction)) +
    facet_grid(cols = vars(reward_condition)) +
    geom_point() +
    geom_smooth(method = "lm", aes(fill = abstraction)) +
    scale_color_manual(values = c(color1, color2), name = "Choice Weight") + 
    scale_fill_manual(values = c(color1, color2), name = "Choice Weight") +
    ylab("Total Points Earned") +
    xlab("Choice Weight Magnitude") +
    mem_theme +
    theme(legend.position = "top",
          legend.text = element_text(face = "plain"))
points_beta_plot
```

# Relations between learning and memory

## Model: Does the reward value of individual items relate to memory?
```{r combine learning values and memory}

#compute average value of each item for each participant
learning_values <- learning_data %>%
    select(subject_id, image, approach_reward) %>%
    mutate(approach_points = extract_numeric(approach_reward)) %>%
    group_by(subject_id, image) %>%
    summarize(mean_reward = mean(approach_points, na.rm = T))

learning_values$subject_id <- as.numeric(as.character(learning_values$subject_id))

#get relevant memory data
memory_values <- memory_data %>%
    select(subject_id, image, mem_response, confidence, mem_acc, conf_number, conf_rating, reward_condition, age, age_group) %>%
    mutate(image = noquote(image))

memory_values$image <- as.character(memory_values$image)


#combine with memory
learning_vals_mem <- full_join(learning_values, memory_values, by = c('subject_id', 'image')) %>%
    drop_na()
```

```{r does stimulus value predict memory}

#scale continuous variables
learning_vals_mem$mean_reward_z <- scale_this(learning_vals_mem$mean_reward)
learning_vals_mem$age_z <- scale_this(learning_vals_mem$age)
learning_vals_mem$abs_reward_z <- scale_this(abs(learning_vals_mem$mean_reward))
learning_vals_mem <- learning_vals_mem %>%
    mutate(reward_sign = case_when(mean_reward <= 0 ~ "neg",
                                   mean_reward > 0 ~ "pos"))

#run model
learning_vals_mem_model <- mixed(mem_acc ~ age_z * reward_condition * abs_reward_z * reward_sign + (reward_condition + reward_sign || subject_id),
                                 family = "binomial",
                                 method = "LRT",
                                 data = learning_vals_mem,
                                 expand_re = T,
                                 control = glmerControl(optimizer = "bobyqa"))

nice(learning_vals_mem_model)

# does not converge with all random slopes

#effects of:
# reward 

```

```{r learning points memory display model}

learning_vals_mem_model.glmer <- mixed(mem_acc ~ age_z * reward_condition * abs_reward_z * reward_sign + (reward_condition + reward_sign || subject_id),
                                 family = "binomial",
                                 method = "LRT",
                                 data = learning_vals_mem,
                                 expand_re = T,
                                 control = glmerControl(optimizer = "bobyqa"),
                                 return = "merMod")

tab_model_glmer(learning_vals_mem_model.glmer)
```

```{r learning points and memory plot}

learning_vals_mem <- learning_vals_mem %>%
    mutate(mean_reward_bin = ntile(mean_reward, 10),
           abs_reward_bin = ntile(abs(mean_reward), 10))

learning_vals_mem_means <- learning_vals_mem %>%
    group_by(mean_reward_bin, reward_condition) %>%
    summarize(mean_acc = mean(mem_acc, na.rm = T),
              mean_conf = mean(conf_rating, na.rm = T))

learning_vals_mem_means2 <- learning_vals_mem %>%
    group_by(mean_reward_bin, reward_condition, age_group) %>%
    summarize(mean_acc = mean(mem_acc, na.rm = T),
              mean_conf = mean(conf_rating, na.rm = T))

learning_vals_mem_plot <- ggplot(learning_vals_mem_means, aes(x = mean_reward_bin, y = mean_acc)) +
    facet_wrap(~reward_condition) +
    geom_point(color = color2) + 
    geom_smooth(method = "lm", color = color3, fill = color3) +
    xlab("Mean Reward Value (Binned)") +
    ylab("Mean Memory Accuracy") +
    mem_theme
learning_vals_mem_plot 

learning_vals_mem_age_plot <- ggplot(learning_vals_mem_means2, aes(x = mean_reward_bin, y = mean_acc)) +
    facet_wrap(~reward_condition * age_group) +
    geom_point(color = color2) + 
    geom_smooth(method = "lm", color = color3, fill = color3) +
    xlab("Mean Reward Value (Binned)") +
    ylab("Mean Memory Accuracy") +
    mem_theme
learning_vals_mem_age_plot 

```

## Do points earned during learning relate to memory?
```{r auc points data processing}

#select relevant variables from beta_ests_points
points_earned <- beta_ests_points %>%
    select(total_points, subject_id, reward_condition) %>%
    unique()

#select relevant variables from memory data
temp <- aucs %>%
    select(subject_id, memory_delay, reward_condition, abstraction = foil_type, age_group, age, AUC)

#convert subject id to factor
temp$subject_id <- factor(temp$subject_id)

#join data
auc_beta_points <- full_join(temp, points_earned, by = c("subject_id", "reward_condition"))
```

### Model: AUC by points earned
```{r fit auc points model}

#does the number of points participants earned in each block relate to memory performance?
auc_beta_points$age_scaled <-scale_this(auc_beta_points$age)
auc_beta_points$points_scaled  <-scale_this(auc_beta_points$total_points)

auc_beta_points_model <- mixed(AUC ~ age_scaled * points_scaled * abstraction * reward_condition + (1|subject_id),
                                  method = "S",
                                  data = auc_beta_points)
nice(auc_beta_points_model) 
summary(auc_beta_points_model)

# Effects
# points
# abstraction
# reward condition
# points x abstraction x reward condition
```

```{r display auc points model}

auc_beta_points_model.lmer <- mixed(AUC ~ age_scaled * points_scaled * abstraction * reward_condition + (1|subject_id),
                                  method = "S",
                                  data = auc_beta_points,
                                  return = "merMod")

tab_model_glmer(auc_beta_points_model.lmer)
```

### Figure 3B: AUC by performance group and reward condition
```{r auc points participant plot, fig.height = 7, fig.width = 4}

auc_beta_points <- auc_beta_points %>%
    group_by(reward_condition) %>%
    mutate(performance_group = ntile(total_points, 2))

auc_beta_points$performance_group <-
    factor(
        auc_beta_points$performance_group,
        levels = c(1, 2),
        labels = c("low point-earners", "high point-earners")
    )

auc_beta_points_means <- auc_beta_points %>%
    group_by(performance_group, abstraction, reward_condition) %>%
    summarize(
        mean_auc = mean(AUC, na.rm = T),
        N = n(),
        se_auc = sd(AUC) / sqrt(N)
    )

#plot
auc_points_plot <- ggplot(auc_beta_points) +
    facet_grid(cols = vars(performance_group),
               rows = vars(abstraction)) +
    geom_hline(yintercept = .5, linetype = "dashed") +
    geom_point(
        data = auc_beta_points,
        aes(x = reward_condition, color = abstraction, y = AUC),
        shape = 95,
        size = 15,
        alpha = .2
    ) +
    geom_point(
        data = auc_beta_points_means,
        aes(x = reward_condition, y = mean_auc),
        color = "black",
        size = 2
    ) +
    geom_errorbar(
        data = auc_beta_points_means,
        aes(
            x = reward_condition,
            y = mean_auc,
            ymin = mean_auc - se_auc,
            ymax = mean_auc + se_auc
        ),
        color = "black",
        width = .1
    ) +
    geom_line(
        data = auc_beta_points_means,
        aes(x = reward_condition, y = mean_auc, group = performance_group),
        color = "black",
        linewidth = .5
    ) +
    scale_color_manual(values = c(color1, color2), name = "Block Condition") +
    xlab("Block Condition") +
    ylab("Memory Performance (AUC)") +
    scale_y_continuous(limits = c(.3, 1), breaks = c(.3, .5, .7, .9)) +
    mem_theme +
    theme(axis.text.x = element_text(angle = 52, hjust = 1),
          legend.position = "none")
auc_points_plot
```

## Do choice weights relate to memory?

```{r auc beta data processing}

#select relevant beta variables
beta_ests_mem <- beta_ests %>%
    select(subject_id, reward_condition, abstraction, est)

#select relevant memory variables
temp <- aucs %>%
    select(subject_id, memory_delay, reward_condition, abstraction = foil_type, age_group, age, AUC)

```

### Model: AUC by age, exemplar choice weights, specificity, block condition

```{r fit auc exemplar choice weights model}

#get exemplar weights
exemplar_weights <- beta_ests_mem %>%
    filter(abstraction == "exemplar") %>%
    select(subject_id, reward_condition, est)

temp$subject_id <- factor(temp$subject_id)

#join data
auc_beta_exemplar <- full_join(temp, exemplar_weights, by = c("subject_id", "reward_condition"))

#scale relevant variables
auc_beta_exemplar$age_scaled <-scale_this(auc_beta_exemplar$age)
auc_beta_exemplar$beta_scaled <-scale_this(auc_beta_exemplar$est)

#fit model
auc_beta_exemplar_model <- mixed(AUC ~ age_scaled * beta_scaled * abstraction * reward_condition + (1|subject_id),
                                  method = "S",
                                  data = auc_beta_exemplar)
nice(auc_beta_exemplar_model)

#effects of:
# beta
# abstraction
# reward condition
# age x beta
# beta x reward condition
# age x beta x reward condition

```

```{r display auc exemplar choice weights model}

auc_beta_exemplar_model.lmer <- mixed(AUC ~ age_scaled * beta_scaled * abstraction * reward_condition + (1|subject_id),
                                  method = "S",
                                  data = auc_beta_exemplar,
                                  return = "merMod")

tab_model_glmer(auc_beta_exemplar_model.lmer)
```

### Figure 3C: AUC by exemplar choice weights - model effects

```{r plot auc by exemplar choice weights model effects, fig.width = 10}
sjPlot::set_theme( 
    base = theme_classic(),
    legend.item.backcol = "transparent",
    geom.boxoutline.color = "black",
    axis.textsize = 1,
    axis.textcolor = "black",
    axis.title.color = "black",
    axis.title.size = 1.1,
    axis.title.x.vjust = -.25,
    axis.title.y.vjust = 1,
    legend.title.size = 1.05)

plot_model(auc_beta_exemplar_model.lmer, type = "pred",
           terms = c("beta_scaled", "age_scaled", "reward_condition", "abstraction"),
           colors = c("#FFCA4B", "#6364a5", "#45b5aa")) +
    scale_color_manual(values = c(color1, color2, color3), name = "Age",
                       labels = c("~ 11 years old",
                                  "~ 16 years old",
                                  "~ 21 years old"
                                  )) +
        scale_fill_manual(values = c(color1, color2, color3), name = "Age",
                       labels = c("~ 11 years old",
                                  "~ 16 years old",
                                  "~ 21 years old"
                                  )) 
```

### Model: AUC by age, category choice weights, specificity, block condition

```{r fit auc category choice weights model}

#get relevant variables
cat_weights <- beta_ests_mem %>%
    filter(abstraction == "category") %>%
    select(subject_id, reward_condition, est)

#join data
auc_beta_cat <- full_join(temp, cat_weights, by = c("subject_id", "reward_condition")) 

#scale
auc_beta_cat$age_scaled <-scale_this(auc_beta_cat$age)
auc_beta_cat$beta_scaled <-scale_this(auc_beta_cat$est)

#fit model
auc_beta_cat_model <- mixed(AUC ~ age_scaled * beta_scaled * abstraction * reward_condition + (1|subject_id),
                                  method = "S",
                                  data = auc_beta_cat)
nice(auc_beta_cat_model)

# effects of:
# age 
# abstraction
# reward condition
# beta x abstraction

```

```{r display auc category choice weights model}

auc_beta_cat_model.lmer <- mixed(AUC ~ age_scaled * beta_scaled * abstraction * reward_condition + (1|subject_id),
                                  method = "S",
                                  data = auc_beta_cat,
                                  return = "merMod")

tab_model_glmer(auc_beta_cat_model.lmer)
```

### Figure 3C: AUC by category choice weights: model effects

```{r plot auc by cat choice weights model effects, fig.width = 10}

sjPlot::set_theme( 
    base = theme_classic(),
    legend.item.backcol = "transparent",
    geom.boxoutline.color = "black",
    axis.textsize = 1,
    axis.textcolor = "black",
    axis.title.color = "black",
    axis.title.size = 1.1,
    axis.title.x.vjust = -.25,
    axis.title.y.vjust = 1,
    legend.title.size = 1.05)

plot_model(auc_beta_cat_model.lmer, type = "pred",
           terms = c("beta_scaled", "age_scaled", "reward_condition", "abstraction"),
           colors = c("#FFCA4B", "#6364a5", "#45b5aa")) +
    scale_color_manual(values = c(color1, color2, color3), name = "Age",
                       labels = c("~ 11 years old",
                                  "~ 16 years old",
                                  "~ 21 years old"
                                  )) +
        scale_fill_manual(values = c(color1, color2, color3), name = "Age",
                       labels = c("~ 11 years old",
                                  "~ 16 years old",
                                  "~ 21 years old"
                                  )) +
    xlab("") +
    ylab("")
```

### Figure (for presentation): Category and exemplar memory by exemplar choice weights

```{r exemplar choice weights and memory}

exemplar_choice_weight_mem_plot <- ggplot(auc_beta_exemplar, aes(x = beta_scaled, y = AUC, color = abstraction)) +
    geom_point() +
    geom_smooth(method = lm, aes(fill = abstraction)) +
    xlab("Exemplar Choice Weight") +
    ylab("Memory Performance") +
    scale_color_manual(values = c(color1, color2), name = "Memory Specificity") +
    scale_fill_manual(values = c(color1, color2), name = "Memory Specificity") +
    mem_theme
exemplar_choice_weight_mem_plot

```

```{r exemplar choice weights and memory by age group, fig.width = 10}

exemplar_choice_weight_mem_age_plot <- ggplot(auc_beta_exemplar, aes(x = beta_scaled, y = AUC, color = abstraction)) +
    facet_wrap(~age_group, scales = "free") +
    geom_point() +
    geom_smooth(method = lm, aes(fill = abstraction)) +
    xlab("Exemplar Choice Weight") +
    ylab("Memory Performance") +
    scale_color_manual(values = c(color1, color2), name = "Memory Specificity") +
    scale_fill_manual(values = c(color1, color2), name = "Memory Specificity") +
    mem_theme
exemplar_choice_weight_mem_age_plot

```

### Figure (for presentation): Category and exemplar memory by category choice weights

```{r category choice weights and memory}

cat_choice_weight_mem_plot <- ggplot(auc_beta_cat, aes(x = beta_scaled, y = AUC, color = abstraction)) +
    geom_point() +
    geom_smooth(method = lm, aes(fill = abstraction)) +
    xlab("Category Choice Weight") +
    ylab("Memory Performance") +
    scale_color_manual(values = c(color1, color2), name = "Memory Specificity") +
    scale_fill_manual(values = c(color1, color2), name = "Memory Specificity") +
    mem_theme
cat_choice_weight_mem_plot

```

```{r category choice weights and memory by age group, fig.width = 10}

cat_choice_weight_mem_age_plot <- ggplot(auc_beta_cat, aes(x = beta_scaled, y = AUC, color = abstraction)) +
    facet_wrap(~age_group, scales = "free") +
    geom_point() +
    geom_smooth(method = lm, aes(fill = abstraction)) +
    xlab("Category Choice Weight") +
    ylab("Memory Performance") +
    scale_color_manual(values = c(color1, color2), name = "Memory Specificity") +
    scale_fill_manual(values = c(color1, color2), name = "Memory Specificity") +
    mem_theme
cat_choice_weight_mem_age_plot

```

# Relations between age and other model parameters

## Model: Initial Q values by age

```{r initial Q values by age model}

#scale age
param_ests$age_scaled <- scale_this(param_ests$age)

#run model
q_init_model <- lm(q_init ~ age_scaled, data = param_ests)
pander(summary(q_init_model))

#significant effect of age

tab_model_glmer(q_init_model)
```

## Supplementary Figure: Initial Q values by age

```{r plot initial Q values, fig.width = 4}

initial_q_plot <- ggplot(param_ests, aes(x = age, y = q_init)) +
    geom_point(color = color3) +
    geom_smooth(method = "lm", color = "black", fill = "black") +
    xlab("Age (Years)") +
    ylab("Initial Q Value") +
    mem_theme
initial_q_plot   
```

## Model: Alpha values by age
```{r alpha values by age model}

#run model
alpha_model <- lm(alpha ~ age_scaled, data = param_ests)
pander(summary(alpha_model))

#no effect of age

tab_model_glmer(alpha_model)
```



