---
title: 'Memory Specificity: Experiment 1 Posterior Predictive Checks'
author: "Kate Nussenbaum"
date: "6/13/24"
output: 
  html_document:
    df_print: paged
    theme: flatly
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{=html}
<style type="text/css">
h1.title {
font-size: 38px;
}
h1 { /* Header 1 */
font-size: 28px;
}
h2 { /* Header 2 */
font-size: 22px;
}
h3 { /* Header 3 */
font-size: 18px;
}

</style>
```

------------------------------------------------------------------------

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, cache = T)
knitr::opts_chunk$set(fig.path = "figures/simulated_data/")
knitr::opts_chunk$set(fig.height = 4, dpi = 600)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```


```{r load needed libraries}
library(tidyverse)
library(glue)
library(ggpubr)
library(pander)
```

```{r define functions}
scale_this <- function(x){
  (x - mean(x, na.rm=TRUE)) / sd(x, na.rm=TRUE)
}

se <- function(x){
    sd(x, na.rm = T)/sqrt(length(x))
}
```

```{r plot theme}
#define colors to use for plots
color4 =  "#d94f70"
color5 = "#f88f58"
color3 = "#45b5aa"
color1 = "#FFCA4B"
color2 = "#6364a5"

#define plotting theme
mem_theme <- theme(panel.background = element_rect(fill='transparent'),
                   axis.line = element_line(color='black'),
                   panel.border = element_rect(color = 'black', fill = "transparent"),
                   panel.grid.minor = element_line(color='transparent'),
                   axis.title.x = element_text(size=14, vjust=-.25),
                   axis.title.y = element_text(size=14, vjust=1),
                   axis.text.x = element_text(size=10, colour="black"),
                   axis.text.y = element_text(size=10, colour="black"),
                   legend.text=element_text(size=12),
                   legend.title = element_text(size = 14),
                   plot.title = element_text(size=16, face = "bold", hjust = .5), 
                   strip.text.x = element_text(size=12), 
                   strip.text.y = element_text(size=12), 
                   strip.background = element_rect(colour= "black", fill = "transparent"))
```

# Import and process data 
```{r import age data}

#read in subject ages
sub_ages <- read_csv('data/e1_sub_ages.csv') 

#create list of all included subjects with subject ids, age, age group
subject_list <- sub_ages %>%
    mutate(age = as.numeric(age)) %>%
    mutate(age_group = case_when(age < 13 ~ "Children",
                                 age >= 13 & age < 18 ~ "Adolescents",
                                 age >= 18 ~ "Adults")) %>%
    mutate(age_group = factor(age_group, levels = c("Children", "Adolescents", "Adults")))

```

```{r import and format empirical learning data}
learning_data <- read_csv('data/e1_learning_data.csv')  %>%
    mutate(reward_condition = as.factor(case_when(block_condition == 1 ~ "Category-Predictive",
                                        block_condition == 2 ~ "Exemplar-Predictive"))) %>%
    group_by(subject_id, task_block, stimulus) %>% 
    mutate(stimulus_repetition = rank(trial_index)) %>%
    ungroup() %>%
    mutate(correct_response = case_when(block_condition == "1" & cat_type == "good" ~ "1",
                                        block_condition == "1" & cat_type == "bad" ~ "0",
                                        block_condition == "1" & cat_type == "neutral" ~ "0",
                                        block_condition == "2" & approach_reward > 0 ~ "1",
                                        block_condition == "2" & approach_reward < 0 ~ "0"),
           correct_response_made = case_when(key_press == correct_response ~ 1,
                                             key_press != correct_response ~ 0))

#add within-block trial and within-condition block order
learning_data <- learning_data %>%
    group_by(subject_id, task_block) %>%
    mutate(learning_trial = rank(trial_index)) %>%
    ungroup() %>%
    group_by(subject_id, block_condition) %>%
    mutate(within_condition_block_num = as.numeric(factor(rank(block_order))))

# add age
learning_data <- full_join(learning_data, subject_list, by = c('subject_id'))

#factor subject id
learning_data$subject_id <- factor(learning_data$subject_id)

```


```{r read in simulated data}

sim_data_folder = "data/sim_data/"

#Read in RL simulations - fourB_oneQ
data_files <- list.files(path = sim_data_folder, pattern = "fourB_oneQ")

sim_data4B <- data.frame()
for (i in c(1:length(data_files))) {
    sim_sub_data <- read_csv(glue("{sim_data_folder}/{data_files[i]}"), show_col_types = F) %>%
        mutate(model = "fourB_oneQ") %>%
        rename(subject_id = ID)
    sim_data4B <- rbind(sim_data4B, sim_sub_data)
}

#Read in RL simulations - twoB_oneQ
data_files <- list.files(path = sim_data_folder, pattern = "twoB_oneQ")

sim_data2B <- data.frame()
for (i in c(1:length(data_files))) {
    sim_sub_data <- read_csv(glue("{sim_data_folder}/{data_files[i]}"), show_col_types = F) %>%
        mutate(model = "twoB_oneQ") %>%
        rename(subject_id = ID)
    sim_data2B <- rbind(sim_data2B, sim_sub_data)
}

#Read in RL simulations - oneB_oneQ
data_files <- list.files(path = sim_data_folder, pattern = "oneB_oneQ")

sim_data1B <- data.frame()
for (i in c(1:length(data_files))) {
    sim_sub_data <- read_csv(glue("{sim_data_folder}/{data_files[i]}"), show_col_types = F) %>%
        mutate(model = "oneB_oneQ") %>%
        rename(subject_id = ID)
    sim_data1B <- rbind(sim_data1B, sim_sub_data)
}

#combine simulated data
sim_data <- rbind(sim_data1B, sim_data2B) %>%
    rbind(., sim_data4B) 

sim_data$subject_id <- factor(sim_data$subject_id)

```

```{r combine simulated and real data}

#combine simulated data with real data
temp <- inner_join(learning_data, sim_data, by = c("subject_id", "block_order", "learning_trial"))  %>%
    mutate(sim_key_press = case_when(sim_choice == 1 ~ 1,
                                     sim_choice == 2 ~ 0),
           correct_response_made = case_when(sim_key_press == correct_response ~ 1,
                                             sim_key_press != correct_response ~ 0))


#add model to empirical data
empirical_data <- learning_data %>%
    mutate(model = "empirical")

#combine simulated and empirical data
sim_learning_data <- rbind(temp, empirical_data)

#factor model and reorder levels
sim_learning_data$model <- factor(sim_learning_data$model, levels = c("empirical", "fourB_oneQ", "twoB_oneQ", "oneB_oneQ"))

```

# Simulated learning

## Plot: Optimal responses across age groups and reward conditions
```{r plot optimal responses by age group and reward condition}

# Plot correct response as a function of reward condition
correct_response_summary_sub <- sim_learning_data %>%
    filter(block_condition == "2" | cat_type != "neutral") %>%
    filter(rt > 0) %>%
    group_by(reward_condition, subject_id, age_group, model) %>%
    summarize(mean_correct = mean(correct_response_made, na.rm = T))

correct_response_summary <- correct_response_summary_sub  %>%
    group_by(reward_condition, age_group, model) %>%
    summarize(group_mean_correct = mean(mean_correct, na.rm = T),
              se_correct = se(mean_correct))

#plot
correct_response_plot <- ggplot(
    correct_response_summary,
    aes(x = reward_condition, fill = model, y = group_mean_correct)
) +
    facet_grid(cols = vars(age_group)) +
    geom_bar(stat = "identity", position = "dodge", color = 'black') +
    geom_errorbar(
        aes(ymin = group_mean_correct - se_correct, ymax = group_mean_correct + se_correct),
        width = .1,
        position = position_dodge(width = .9)
    ) +
    xlab("Block Condition") +
    ylab("Proportion of Correct Responses") +
    scale_fill_manual(
        values = c('gray30', color3, color4, color5),
        labels = c("empirical", expression(four ~ beta, two ~
                                               beta, one ~ beta)),
        name = "Model"
    ) +
    geom_hline(yintercept = .5, linetype = "dashed") +
    coord_cartesian(ylim = c(.4, .9)) +
    mem_theme +
    theme(legend.position = "top",
          axis.text.x = element_text(angle = 35, hjust = 1))
correct_response_plot
```


## Plot: Optimal responses across trials, age groups, and reward conditions (winning model only)
```{r plot optimal responses by trial age group and reward condition}

# Plot correct response as a function of reward condition and stimulus repetition 
correct_response_summary_sub <- sim_learning_data %>%
    filter(block_condition == "2" | cat_type != "neutral") %>%
    filter(rt > 0) %>%
    filter(model %in% c('empirical', 'fourB_oneQ')) %>%
    group_by(reward_condition, stimulus_repetition, subject_id, age_group, model) %>%
    summarize(mean_correct = mean(correct_response_made, na.rm = T))

correct_response_summary <- correct_response_summary_sub  %>%
    group_by(reward_condition, stimulus_repetition, age_group, model) %>%
    summarize(group_mean_correct = mean(mean_correct, na.rm = T),
              se_correct = se(mean_correct))

#group means
correct_response_plot <- ggplot(correct_response_summary, 
                                    aes(x = stimulus_repetition, 
                                        color = reward_condition,
                                        y = group_mean_correct)) +
    facet_grid(cols = vars(age_group), rows = vars(model)) +
    geom_point() +
    geom_line() +
    geom_errorbar(aes(ymin = group_mean_correct - se_correct, ymax = group_mean_correct + se_correct), 
                  width = .1) + 
    xlab("Stimulus Repetition") +
    ylab("Proportion of Correct Responses") +
    scale_color_manual(values = c(color1, color2),
                       name = "Block Condition") + 
    geom_hline(yintercept = .5, linetype = "dashed") +
    scale_y_continuous(breaks = c(.5, .7, .9)) +
    mem_theme +
    theme(legend.position = "top")
correct_response_plot
```


## Plot: Generalization (response to first appearance of each stimulus)by age group and reward condition 
```{r plot generalization by age group and reward condition}

# add category to learning data frame
sim_learning_data <- sim_learning_data %>%
    separate(stimulus,
             into = c(NA, "image"),
             sep = "/") %>%
    mutate(stim_num = parse_number(image)) %>%
    separate(image,
             into = c("category", NA),
             sep = "([12345678])",
             remove=FALSE)

# determine category repetition number
sim_learning_data <- sim_learning_data %>%
    group_by(subject_id, task_block, category, age_group, model) %>%
    mutate(category_rep = rank(trial_index))

# determine correct responses as a function of stimulus rep and category rep
correct_response_category_rep <- sim_learning_data %>%
    filter(block_condition == "2" | cat_type != "neutral") %>%
    filter(rt > 0) %>%
    group_by(reward_condition, stimulus_repetition, age_group, model) %>%
    summarize(group_mean_correct = mean(correct_response_made, na.rm = T),
              se_correct = se(correct_response_made))  %>%
    filter(stimulus_repetition == 1)

#plot
correct_response_generalization_plot <- ggplot(
    correct_response_category_rep,
    aes(x = reward_condition, fill = model, y = group_mean_correct)
) +
    facet_grid(cols = vars(age_group)) +
    geom_bar(stat = "identity", position = "dodge", color = 'black') +
    geom_errorbar(
        aes(ymin = group_mean_correct - se_correct, ymax = group_mean_correct + se_correct),
        width = .1,
        position = position_dodge(width = .9)
    ) +
    xlab("Block Condition") +
    ylab("Correct Responses to 1st Stim.") +
    scale_fill_manual(
        values = c('gray30', color3, color4, color5),
        name = "Model",
        labels = c("empirical", expression(four ~ beta, two ~
                                               beta, one ~ beta))
    ) +
    geom_hline(yintercept = .5, linetype = "dashed") +
    mem_theme +
    theme(legend.position = "top",
          axis.text.x = element_text(angle = 35, hjust = 1)) +
    coord_cartesian(ylim = c(.4, .8))
correct_response_generalization_plot
```

## Plot: Category WSLS across age groups and reward conditions

```{r category win stay lose shift data processing}

#first determine prior response and prior reward to previous category appearance
temp2 <- sim_learning_data %>% 
    filter(model != "empirical") %>%
    group_by(subject_id, block_order, category, model) %>%
    mutate(prior_cat_stim = lag(image), #previous stimulus
           prior_cat_response = lag(sim_key_press), #previous response
           prior_cat_correct_response_made = lag(correct_response_made), #previous outcome (win or lose) 
           category_stay = case_when(prior_cat_response == sim_key_press ~ 1,
                                prior_cat_response != sim_key_press ~ 0),
           same_stim = case_when(image == prior_cat_stim ~ 1,
                                 image != prior_cat_stim ~ 0)) %>%
    ungroup() %>%
        mutate(WSLS = case_when(prior_cat_correct_response_made == 1 & category_stay == 1 ~ 1, 
                            prior_cat_correct_response_made == 1 & category_stay == 0 ~ 0,
                            prior_cat_correct_response_made == 0 & category_stay == 1 ~ 0, 
                            prior_cat_correct_response_made == 0 & category_stay == 0 ~ 1))

temp3 <- sim_learning_data %>% 
    filter(model == "empirical") %>%
    group_by(subject_id, block_order, category, model) %>%
    mutate(prior_cat_stim = lag(image), #previous stimulus
           prior_cat_response = lag(key_press), #previous response
           prior_cat_correct_response_made = lag(correct_response_made), #previous outcome (win or lose) 
           category_stay = case_when(prior_cat_response == key_press ~ 1,
                                prior_cat_response != key_press ~ 0),
           same_stim = case_when(image == prior_cat_stim ~ 1,
                                 image != prior_cat_stim ~ 0)) %>%
    ungroup() %>%
        mutate(WSLS = case_when(prior_cat_correct_response_made == 1 & category_stay == 1 ~ 1, 
                            prior_cat_correct_response_made == 1 & category_stay == 0 ~ 0,
                            prior_cat_correct_response_made == 0 & category_stay == 1 ~ 0, 
                            prior_cat_correct_response_made == 0 & category_stay == 0 ~ 1))

sim_wsls_data <- rbind(temp2, temp3)

```

```{r plot wsls by age group and reward condition}

#determine win-stay lose shift behavior across age group and blocks
win_stay_lose_shift_sub_means <- sim_wsls_data %>%
    filter(same_stim == 0) %>% #different stim only
    group_by(subject_id, age, age_group, reward_condition, model) %>%
    summarize(mean_sub_WSLS = mean(WSLS, na.rm = T),
              se_sub_WSLS = se(WSLS)) %>%
    drop_na()

win_stay_lose_shift_means <- win_stay_lose_shift_sub_means %>%
    group_by(age_group, reward_condition, model) %>%
    summarize(mean_WSLS = mean(mean_sub_WSLS, na.rm = T),
              se_WSLS = se(mean_sub_WSLS)) %>%
    drop_na()

#plot
WSLS_simple_plot <- ggplot(win_stay_lose_shift_means,
                           aes(x = reward_condition, y = mean_WSLS, fill = model)) +
    facet_grid(cols = vars(age_group)) +
    geom_bar(stat = "identity", position = "dodge", color = 'black') +
    geom_errorbar(
        width = .1,
        position = position_dodge(width = .9),
        aes(ymin = mean_WSLS - se_WSLS, ymax = mean_WSLS + se_WSLS)
    ) +
    scale_fill_manual(
        values = c('gray30', color3, color4, color5),
        labels = c("empirical", expression(four ~ beta, two ~
                                               beta, one ~ beta)),
        name = "Model"
    ) +
    geom_hline(yintercept = .5, linetype = "dashed") +
    xlab("Block Condition") +
    ylab("Category WSLS") +
    mem_theme +
    theme(legend.position = "top",
          axis.text.x = element_text(angle = 35, hjust = 1)) +
    coord_cartesian(ylim = c(.4, .8))
WSLS_simple_plot 
```



## Plot generalization (winning model only)
```{r generalization plot}

correct_response_category_rep <- sim_learning_data %>%
    filter(model %in% c('empirical', 'fourB_oneQ')) %>%
    filter(block_condition == "2" | cat_type != "neutral") %>%
    filter(rt > 0) %>%
    group_by(reward_condition, category_rep, stimulus_repetition, age_group, model) %>%
    summarize(group_mean_correct = mean(correct_response_made, na.rm = T),
              se_correct = se(correct_response_made))  %>%
    filter(stimulus_repetition == 1)

correct_response_category_rep_plot <- ggplot(correct_response_category_rep, 
                                aes(x = category_rep,
                                    color = reward_condition,
                                    y = group_mean_correct)) +
    facet_grid(cols = vars(age_group), rows = vars(model)) +
    geom_point() +
    geom_line(aes(group = reward_condition)) +
    geom_errorbar(aes(ymin = group_mean_correct - se_correct, ymax = group_mean_correct + se_correct), 
                  width = .1) + 
    xlab("Category Repetition") +
    ylab("Correct Responses to 1st Stim.") +
    scale_color_manual(values = c(color1, color2),
                       name = "Block Condition") + 
    geom_hline(yintercept = .5, linetype = "dashed") +
    mem_theme  +
    theme(legend.position = "top")
correct_response_category_rep_plot
```


## WSLS (winning model only)
```{r wsls}

#determine win-stay lose shift behavior across age group and blocks
win_stay_lose_shift_sub_means <- sim_wsls_data %>%
    filter(model %in% c('empirical', 'fourB_oneQ')) %>%
    filter(same_stim == 0) %>% #different stim only
    mutate(trial_group = ntile(learning_trial, 3)) %>%
    group_by(trial_group, subject_id, age, age_group, reward_condition, model) %>%
    summarize(mean_sub_WSLS = mean(WSLS, na.rm = T),
              se_sub_WSLS = se(WSLS)) %>%
    drop_na()

#plot
WSLS_plot <- ggplot(win_stay_lose_shift_sub_means, aes(x = trial_group, y = mean_sub_WSLS, fill = reward_condition)) +
    facet_grid(cols = vars(age_group), rows = vars(model)) +
    geom_boxplot(data = filter(win_stay_lose_shift_sub_means, trial_group == 1)) + 
    geom_boxplot(data = filter(win_stay_lose_shift_sub_means,  trial_group == 2)) +
    geom_boxplot(data = filter(win_stay_lose_shift_sub_means,  trial_group == 3)) +
    scale_fill_manual(values = c(color1, color2),
                      name = "Block Condition") + 
    scale_color_manual(values = c(color1, color2),
                      name = "Block Condition") + 
    geom_hline(yintercept = .5, linetype = "dashed") +
    xlab("Trial Group (17 trials)") +
    ylab("Category Win-Stay Lose-Shift") +
    scale_x_continuous(breaks = c(1, 2, 3), labels = c(1,2,3)) +
    coord_cartesian(ylim = c(.3, 1)) +
    mem_theme +
    theme(legend.position = "top")
WSLS_plot 
```




